---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

#### 1. ACCESS BABASE
```{r}
#Open 'Utilities'>'Terminal'
#ssh -f mjc107@papio.biology.duke.edu -L 2222:localhost:5432 -N

#Install devtools if not already present
if (!("devtools" %in% installed.packages()[,"Package"]))
  install.packages("devtools")
# Install newest version of ramboseli if not already installed
devtools::install_github("amboseli/ramboseli")
#devtools::install_github("amboseli/ramboseli", ref = "ramboselitidyr-dev")
Sys.setenv(TZ = 'UTC')
list.of.packages <- list("foreach", "doSNOW", "parallel", "tidyverse",
                         "lubridate", "dbplyr", "purrrlyr", "RPostgreSQL",
                         "zoo", "ramboseli")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if (length(new.packages)) install.packages(unlist(new.packages))
lapply(list.of.packages, require, character.only = T)

library(DHARMa)
library(ramboseli)
library(tidyverse)
library(dbplyr)
library(data.table)
library(ggplot2)
library(cowplot)
library(corrplot)
library(vegan)
library(broom.mixed)
library(RcppRoll)
library(stringr)
library(network)
library(intergraph)
library(igraph)
# library(MuMIn)
library(reshape2) 
library(lubridate)
library(hrbrthemes)
library(viridis)
library(forcats)
library(coxme)
library(lme4)
library(car)
library(ggfortify)
library(survival)
library(survminer)
library(patchwork)

# You will need to change user to your personal babase login AND get your password
# One approach to doing that is through Rstudio
# You could also just type it in your script, but that's not recommended for security.
babase <- DBI::dbConnect(RPostgreSQL::PostgreSQL(),
                           host = "localhost",
                           port = 2222,
                           user = "zf59",
                           dbname = "babase",
                           password = rstudioapi::askForPassword("Database password"))

```

#### 2. DATA MANAGEMENT

#### 2.1 LOAD BABASE TABLES

```{r}
#Connect to source functions
source("Functions.R") 

# ---- LOAD DATAFRAMES ------------------------------------------------------

# Database connections
biograph <- tbl(babase, "biograph")
members <- tbl(babase, "members")
maturedates <- tbl(babase, "maturedates")
rankdates <- tbl(babase, "rankdates")
maternities <- tbl(babase, "maternities")
actor_actees <- tbl(babase, "actor_actees")
samples_goff <- tbl(babase, "samples_goff")
groups_history <- tbl(babase, "groups_history")

# Get local copy of biograph table
biograph_l <- collect(tbl(babase, "biograph"))

#Get local copy of maternities table
maternities_l <- collect(tbl(babase, "maternities"))

#Get local copy of groups history table
groups_history_l <- collect(tbl(babase, "groups_history"))

#Get local copy of maturedates
maturedates_l <- collect(tbl(babase, "maturedates"))

#Get local copy of rankdates
rankdates_l <- collect(tbl(babase, "rankdates"))

# ---- JOIN DATAFRAMES ------------------------------------------------------

#Create connection version
# Join maturedates to biograph
md_females <- maturedates %>%
  semi_join(filter(biograph, sex == "F"), by = "sname")

# Join rankdates to biograph
rd_males <- rankdates %>%
  semi_join(filter(biograph, sex == "M"), by = "sname")

#Create local version of md_females and rd_males
# Join maturedates to biograph
md_females_l <- maturedates %>%
  semi_join(filter(biograph, sex == "F"), by = "sname") %>%
  collect()

# Join rankdates to biograph
rd_males_l <- rankdates %>%
  semi_join(filter(biograph, sex == "M"), by = "sname") %>%
  collect()

# ---- SUBSETTED DATASETS EXCLUDING BEHAVIORAL GAPS -------------------------
members_l <- subset_members(babase)
focals_l <- subset_focals(babase, members_l)
females_l <- subset_females(members_l)
grooming_l <- subset_interactions(babase, members_l, my_acts = c("G"))

```

#### 2.2 CREATE DATASET

```{r}

# ---- GRP YEARS -------------------------------------------------------------

#Note: these grp years may need some revision after meetings with Susan and Laurence

# The rows should be:
#   - group years
#   - groups that were study groups during year of interest
#   - exclude group 1.3 (Proton's group
#   - first start date should be the date the grp became a study grp
#   - last end date can't occur after the last time the grp was a study grp

#Create df where group years are level of observation
groups <- groups_history_l %>%
  filter(gid < 3 & gid != 1.3) %>% #eliminate non-study groups
  filter(!is.na(first_study_grp_census)) %>% #Note: check why these are NA but listed as study groups
  select(gid, name, permanent, impermanent, first_study_grp_census, last_reg_census, study_grp) %>%
  mutate(last_time_study_grp = fifelse(!is.na(last_reg_census), as.Date(last_reg_census), 
                                        fifelse(is.na(last_reg_census) & !is.na(impermanent), as.Date(impermanent), as.Date("2022-06-29")))) #create date telling last time grp was a study grp

#Create a start date for each group year
groups <- groups %>%
  mutate(startyear = fifelse(month(first_study_grp_census)==11 | month(first_study_grp_census)==12, as.numeric(format(first_study_grp_census,'%Y')) + 1, as.numeric(format(first_study_grp_census,'%Y'))))
  
groups$first_start <- as.Date(paste(groups$startyear, 11, 1), "%Y %m %d")

#Create a start date for each group year - if you want to start each year on day group first censused
start_dates <- groups %>%
  rowwise() %>%
  do(data.frame(gid=.$gid, start=seq(.$first_start,.$last_time_study_grp,by="1 year")))

#Create a start date for each group year - if you want to start each year on day group first censused
#start_dates <- groups %>%
#  rowwise() %>%
#  do(data.frame(gid=.$gid, start=seq(.$first_study_grp_census,.$last_time_study_grp,by="1 year")))

#Create group year df with start and end date for each year
group_years <- groups %>%
  dplyr::left_join(select(start_dates, "gid", "start"), by = "gid") %>% #join start dates
  mutate(end = start + years(1) - days(1),
         grp_year_length = end - start) %>%
  filter(end < last_time_study_grp) #end date can't occur after the last time the grp was a study grp


```

#### 3. CALCULATE VARIABLES FOR ANALYSIS

#### 3.1 NETWORK DENSITY AND GROUP SIZE

This is code I wrote to estimate network density and group size for a different analysis. In that analysis infant baboons were the level of observation and the start and end dates were a six month window during their early life. The df that held all my final data was called "subjects" which is here the equivalent of our "group_years" df. This code needs to be adapted to estimate network density for each group year.

n_adults = group size (we will also want to separate this by sex e.g., n_adults_female and n_adults_male)
net_density_wog = network density

Resources I used:
https://towardsdatascience.com/how-to-model-a-social-network-with-r-878b3a76c5a1
http://pablobarbera.com/big-data-upf/html/02a-networks-intro-visualization.html

```{r}

# Find all adult members in each group on each date
adult_members <- members %>%
  filter(grp < 3 & grp != 1.3) %>%
  inner_join(select(biograph, sname, sex), by = "sname") %>%
  left_join(select(md_females, sname, matured), by = "sname") %>%
  left_join(select(rd_males, sname, ranked), by = "sname") %>%
  filter((sex == "F" & date >= matured) | (sex == "M" & date >= ranked)) %>%
  collect()

#Network density without individuals with no grooms
grpyr_df <- group_years %>% 
  rowwise() %>% 
  mutate(sub_groom_df = list(subset_grooming(gid, start, end))) %>% 
  ungroup()

grpyr_df <- grpyr_df %>% 
  rowwise() %>% 
  mutate(sub_members_df = list(subset_membership_WITHOUT183(gid, start, end))) %>% 
  ungroup()

#Count number of grooms in groups
grpyr_df <- grpyr_df %>%
  mutate(groom_rows = sapply(sub_groom_df, NROW)) %>% #Find number of rows in each sub_groom_df
  filter(groom_rows != "0") #eliminate grps with no grooms in their group due to behave gaps

#NOTE: This df still includes some behavioural gaps, where some grooming data has been recorded - we should decide what to do about these (we will control for observer effort later on)

#Count number of members in group >= 183 days to get group size
grpyr_df <- grpyr_df %>%
  mutate(n_adults = sapply(sub_members_df, NROW))

grpyr_df <- grpyr_df %>%
  mutate(net_density_wog = map2_dbl(sub_groom_df, sub_members_df, get_net_density_wog)) #network density including individuals with no grooms

#Join grpyr_df to subjects on mom_sname and end date
group_years <- group_years %>%
  left_join(select(grpyr_df, gid, end, n_adults, net_density_wog, sub_members_df), by = c("gid", "end")) %>%
  mutate(net_density_wog = as.numeric(net_density_wog))


#### 1. Example network: Low network density

#Practice on one dataframe
#Subset grooming dataframe by group and time period
edges_sna_df <- subset(grooming_l, as.Date("2010-10-20") <= date & date <= as.Date("2011-10-19") & actor_grp==1.1100 & actee_grp==1.1100)

edges.df <- edges_sna_df %>%
  select(actor, actee) %>% #need actor, actee, total grooms
  mutate(pairs = paste(actor, actee))

edges.df <- edges.df %>%
  count(pairs) %>%
  mutate(actor = str_sub(pairs, 1, 3),
         actee = str_sub(pairs, 5, 7)) %>% 
  rename(weight = n) %>% 
  select(actor, actee, weight, -pairs)

#Create nodes df - Does include individuals with no grooms
nodes_sna_df <- subset(adult_members, as.Date("2010-10-20") <= date & date <= as.Date("2011-10-19") & grp==1.1100)

nodes.df <- nodes_sna_df %>%
  rename(name = sname) %>%
  distinct(name,.keep_all = TRUE) %>%
  select(name, sex)
nodes.df$id <- 1:nrow(nodes.df)

#my_network <- graph_from_data_frame(d=edges.df, vertices=nodes.df, directed=FALSE) #creates multiplex network
my_network <- graph_from_data_frame(d=edges.df, vertices=nodes.df, directed=TRUE)

#Plot example network
V(my_network)$color <- NA
males <- nodes.df %>% filter(sex == "M")
females <- nodes.df %>% filter(sex == "F")
V(my_network)$color[V(my_network)$name %in% males$name] <- "cyan4"
V(my_network)$color[V(my_network)$name %in% females$name] <- "darkseagreen2"
vertex_attr(my_network)

V(my_network)$size <- sqrt(strength(my_network)) * 1.1
set.seed(270)
fr <- layout_with_fr(my_network, niter=1000)
par(mar=c(0,0,0,0)); plot(my_network, layout=fr, vertex.label.color=c("black"))
title("", adj = 0, line = -1)
legend(x=.75, y=.85, legend=c("Male", "Female"), 
       pch=21, pt.bg=c("cyan4", "darkseagreen2"), pt.cex=2, bty="n")

#Calculate network density
my_network <- asNetwork(my_network)
network_density <- network::network.density(my_network)

```

#### 3.2 OBSERVER EFFORT

```{r}

# ---- OBSERVER EFFORT ------------------------------------------------------

#After 1999-10-04
#Grp focal minutes per adult
adult_focals <- samples_goff %>%
  filter(grp_of_focal < 3 & grp_of_focal != 1.3) %>%
  inner_join(select(biograph, sname, sex), by = "sname") %>%
  left_join(select(md_females, sname, matured), by = "sname") %>%
  left_join(select(rd_males, sname, ranked), by = "sname") %>%
  filter((sex == "F" & date >= matured) | (sex == "M" & date >= ranked)) %>%
  collect()

#Join to subjects - zeros because no focal data in samples_goff before 1999-10-04
group_years <- group_years %>%
  rowwise() %>%
  mutate(grp_focal_mins_post1999=get_focal_mins(adult_focals, start, end, gid))


#Before 1999-10-04 - Note: there are some imperfections in these data in babase
# Database connections
a1 <- tbl(babase, in_schema("babase_pending", "altos_points_84to96mar3")) %>%
  collect()
names(a1)[6:8] <- c("nn", "n1", "n2")
a1$n2 <- str_trim(a1$n2)
a2 <- tbl(babase, in_schema("babase_pending", "altos_points_96marto99")) %>%
  collect()
names(a2)[6:8] <- c("nn", "n1", "n2")
h1 <- tbl(babase, in_schema("babase_pending", "hooks_points_84to96")) %>%
  collect()
names(h1)[6:8] <- c("nn", "n1", "n2")
h2 <- tbl(babase, in_schema("babase_pending", "hooks_points_96to99")) %>%
  collect()
names(h2)[6:8] <- c("nn", "n1", "n2")
# Combine into one
samples_pre1999 <- bind_rows(select(a1, -mpos),
                  select(a2, -mpos),
                  select(h1, -mpos),
                  select(h2, -mpos))

#Create local version of members with behave gaps included
members_l3 <- collect(tbl(babase, "members"))

#Focal minute totals for individuals each hour
adult_focals_pre1999 <- samples_pre1999 %>%
  group_by(sname, date, time) %>%
  tally() %>%
  ungroup()

#Grp focal minutes per adult
adult_focals_pre1999 <- adult_focals_pre1999 %>%
  left_join(select(members_l3, sname, date, "grp_of_focal" = "grp"), by = c("sname", "date")) %>%
  filter(grp_of_focal < 3 & grp_of_focal != 1.3) 

adult_focals_pre1999 <- adult_focals_pre1999 %>%
  inner_join(select(biograph_l, sname, sex), by = "sname") %>%
  left_join(select(md_females_l, sname, matured), by = "sname") %>%
  left_join(select(rd_males_l, sname, ranked), by = "sname") %>%
  filter((sex == "F" & date >= matured) | (sex == "M" & date >= ranked)) %>%
  rename("minsis" = "n")  %>%
  collect()

#Join to subjects - focal data from before 1999-10-04
group_years <- group_years %>%
  rowwise() %>%
  mutate(grp_focal_mins_pre1999=get_focal_mins(adult_focals_pre1999, start, end, gid))

#Calculate group observation effort
group_years <- group_years %>%
  mutate(obs_effort = ifelse(start < as.Date("1999-10-04"), as.numeric(grp_focal_mins_pre1999)/n_adults, as.numeric(grp_focal_mins_post1999)/n_adults)) 

grpyr_df<-grpyr_df%>%
  dplyr::left_join(select(group_years, "gid", "start", "obs_effort"), by = c("gid", "start"))



# ---- CREATE RESIDUAL NETWORK DENSITY --------------------------------------------

#NOTE: This does not run because some individuals get NAs for observer effort - we need to look into why this is

#Make residual net density residuals
l1<- lm(log(net_density_wog)~log(obs_effort),data=grpyr_df)
grpyr_df$net_density_wog_resid<- resid(l1)

#Group size vs DSI (females)
ggplot(grpyr_df, aes(x=n_adults, y=net_density_wog_resid)) +
      geom_point(size = 2.0, alpha = 0.7, colour="violetred4") +
      theme_cowplot() +
      ylab("Network density resid") +
      xlab("Group size") +
      geom_smooth(method=lm, colour="black", size=0.5)
p1.m <- lm(net_density_wog_resid ~ n_adults, data=grpyr_df)


```

#### 3.3 Calculate Foraging Efficiency


```{r}
# CALCULATE POINT SAMPLES
# Point sample data are in the old formats in babase_pending
# In four different tables, which oddly have different column names
# for proximity columns (so rename below)

a1 <- tbl(babase, in_schema("babase_pending", "altos_points_84to96mar3")) %>%
  collect()
names(a1)[6:8] <- c("nn", "n1", "n2")
a1$n2 <- str_trim(a1$n2)

a2 <- tbl(babase, in_schema("babase_pending", "altos_points_96marto99")) %>%
  collect()
names(a2)[6:8] <- c("nn", "n1", "n2")

h1 <- tbl(babase, in_schema("babase_pending", "hooks_points_84to96")) %>%
  collect()
names(h1)[6:8] <- c("nn", "n1", "n2")

h2 <- tbl(babase, in_schema("babase_pending", "hooks_points_96to99")) %>%
  collect()
names(h2)[6:8] <- c("nn", "n1", "n2")


# Combine into one
points_old <- bind_rows(select(a1, -mpos),
                        select(a2, -mpos),
                        select(h1, -mpos),
                        select(h2, -mpos))

#Get local copy of points after 1999
points_new <- collect(tbl(babase, "point_data"))

biograph <-collect(tbl(babase, "biograph"))
members <- collect(tbl(babase, "members"))
samples <- collect(tbl(babase, "samples"))

ex_group<- grpyr_df[[13]][[1]]
ex_group$start[1]
ex_group$end[1]

## WORKING WITH NEW POINTS DATA
# total of point samples for a particular group year row

total_point_samples_gr_new<-function(sub_members_df){
    sub_members_df%>%
    left_join(samples, by="sname")%>%
    left_join(points_new, by ="sid")%>%
    filter(sex == "F")%>%
    filter(date>start&date<end)
}

count_total_new<-function(sub_members_df){
    total_point_samples_gr_new(sub_members_df)%>%
    group_by(sname)%>%
    count()
}

# time   spent   feeding: number of point samples from total sample adult females
count_feeding_new<-function(sub_members_df){
    total_point_samples_gr_new(sub_members_df)%>%
    filter(activity=="F")%>%
    group_by(sname)%>%
    count()
}

# time   spent   moving:  # of point samples from total sample adult females
count_moving_new<-function(sub_members_df){
    total_point_samples_gr_new(sub_members_df)%>%
    filter(activity=="W")%>%
    group_by(sname)%>%
    count()
}

# ## TEST WITH POINT SAMPLE NEW
# group_point <- ex_group%>%
#   left_join(samples, by="sname")%>%
#   left_join(points_new, by ="sid")%>%
#   filter(sex == "F")%>%
#   filter(date>start&date<end)%>%
#   filter(activity=="W")%>%
#   group_by(sname)%>%
#   count()

# count samples from points new in groupyear df
grpyr_df<-grpyr_df%>%
  rowwise() %>% 
  mutate(n_total_sample_new=sum(count_total_new(sub_members_df)$n))%>%
  mutate(n_feeding_new = sum(count_feeding_new(sub_members_df)$n))%>%
  mutate(n_moving_new = sum(count_moving_new(sub_members_df)$n))

## WORKING WITH NEW POINTS DATA
# total of point samples for a particular group year row

total_point_samples_gr_old<-function(sub_members_df){
    sub_members_df%>%
    left_join(points_old, by ="sname")%>%
    filter(sex == "F")%>%
    filter(date>start&date<end)
}

count_total_old<-function(sub_members_df){
    total_point_samples_gr_old(sub_members_df)%>%
    group_by(sname)%>%
    count()
}

# time   spent   feeding: number of point samples from total sample adult females
count_feeding_old<-function(sub_members_df){
    total_point_samples_gr_old(sub_members_df)%>%
    filter(act=="F")%>%
    group_by(sname)%>%
    count()
}

# time   spent   moving:  # of point samples from total sample adult females
count_moving_old<-function(sub_members_df){
    total_point_samples_gr_old(sub_members_df)%>%
    filter(act=="W")%>%
    group_by(sname)%>%
    count()
}

# count samples from points old in groupyear df
grpyr_df<-grpyr_df%>%
  rowwise() %>% 
  mutate(n_total_sample_old=sum(count_total_old(sub_members_df)$n))%>%
  mutate(n_feeding_old = sum(count_feeding_old(sub_members_df)$n))%>%
  mutate(n_moving_old = sum(count_moving_old(sub_members_df)$n))

grpyr_df<-grpyr_df%>%
  mutate(n_total_sample=n_total_sample_new+n_total_sample_old)%>%
  mutate(n_feeding=n_feeding_old+n_feeding_new)%>%
  mutate(n_moving=n_moving_old+n_moving_new)%>%
  select(-n_total_sample_old,-n_feeding_old,-n_moving_old,-n_total_sample_new, -n_feeding_new, -n_moving_new)
```

#### 3.3 RAINFALL VARIABLES
```{r}
# ---- HYDRO YEAR ----------------------------------------------------------

#Get hydroyear of start date
grpyr_df<-grpyr_df%>%
  mutate(hydroyear = get_hydroyear(start))

# ---- RAINFALL ------------------------------------------------------------

amb_rain <- collect(tbl(babase, "min_maxs"))

# Take sum of measurements
amb_rain <- amb_rain %>%
  mutate(date_of = as.Date(wrdaytime)) %>%
  group_by(date_of) %>%
  summarise(rain = sum(rain, na.rm = TRUE)) 

grpyr_df<-grpyr_df%>%
  rowwise() %>%
  mutate(
    rain_normal = get_rain_normal(amb_rain, quo(date_of), quo(rain), start, end), 
    rain_total = get_rain_total(amb_rain, quo(date_of), quo(rain), start, end), 
    rain_anom_yr = rain_total - rain_normal, 
    rain_avg = get_rain_avg(amb_rain, start, end), 
    rain_div = get_rain_var(amb_rain, start, end)) %>%
  ungroup()
  
```
  

#### 3.4 EDA

## Scatterplot

```{r}
p1<-ggplot(data=grpyr_df, aes(x=n_adults, y=n_feeding/n_total_sample)) + geom_point()+labs(x = "Group Size", y="Proportion of Time Spent Feeding", title = "Relationship of group size vs. proportion of time spent feeding")+geom_smooth(method=lm, se=FALSE, col='blue')

p2<-ggplot(data=grpyr_df, aes(x=net_density_wog_resid, y=n_feeding/n_total_sample)) + geom_point()+labs(x = "Network Density", y="Proportion of Time Spent Feeding", title = "Relationship of network density vs. proportion of time spent feeding")+geom_smooth(method=lm, se=FALSE, col='blue')

p3<-ggplot(data=grpyr_df, aes(x=n_adults, y=n_moving/n_total_sample)) + geom_point()+labs(x = "Group Size", y="Proportion of Time Spent Moving", title = "Relationship of group size vs. proportion of time spent moving")+geom_smooth(method=lm, se=FALSE, col='blue')

p4<-ggplot(data=grpyr_df, aes(x=net_density_wog_resid, y=n_moving/n_total_sample)) + geom_point()+labs(x = "Network Density", y="Proportion of Time Spent Moving", title = "Relationship of network density vs. proportion of time spent moving")+geom_smooth(method=lm, se=FALSE, col='blue')

p2
p4
```


## Histogram

```{r}
p3 <- ggplot(grpyr_df, aes(x=n_feeding/n_total_sample)) + geom_histogram(color="black", fill="white")+labs(x = "Age", title = "Distribution of proportion of time spent feeding")
p4 <- ggplot(grpyr_df, aes(x=n_moving/n_total_sample)) + geom_histogram(color="black", fill="white")+labs(x = "Age", title = "Distribution of proportion of time spent moving")
p3+p4
```

```{r}
logis.model.feeding<-glmer(cbind(n_feeding, (n_total_sample-n_feeding)) ~ scale(n_adults)+scale(net_density_wog)+ (1|gid), data=grpyr_df,family = "binomial"(link="logit"))
#logistic regression
summary(logis.model.feeding)
# R squared
# with(summary(logis.model.feeding), 1 - deviance/null.deviance)
```

```{r}
logis.model.moving <- glmer(cbind(n_moving, (n_total_sample-n_feeding)) ~ scale(n_adults)+scale(net_density_wog)+ (1|gid), data=grpyr_df,family = "binomial"(link="logit"))
summary(logis.model.moving)
#logistic regression
```

```{r}
logis.model.feeding_per_moving <- glmer(cbind(n_feeding, n_moving) ~ scale(n_adults)+scale(net_density_wog)+ (1|gid), data=grpyr_df,family = "binomial"(link="logit"))
#logistic regression
summary(logis.model.feeding_per_moving)
```

#### Model diagnostics

```{r}
simulationOutput <- simulateResiduals(fittedModel = logis.model.feeding_per_moving, n = 250)

plot(simulationOutput) # Overall residual check
testDispersion(simulationOutput) # Overdispersion check
testUniformity(simulationOutput = simulationOutput) # Heteroscedasticity check
testZeroInflation(simulationOutput) # Zero inflation check

with(grpyr_df, plot(simulationOutput$scaledResiduals ~ n_adults))
with(grpyr_df, plot(simulationOutput$scaledResiduals ~ net_density_wog))

## odds ratios and 95% CI on odds ratio - if 95% CI on OR includes 1 the predictor is not sig
exp(cbind(OR = coef(logis.model.feeding_per_moving), confint(logis.model.feeding_per_moving)))
```

#### Model Visualizations

```{r}
# Fill predicted values using regression model
grpyr_df$outcome_m1 <- predict(logis.model.feeding, grpyr_df, type="response")
# Plot Predicted data and original data points
ggplot(data=grpyr_df, aes(x=n_adults, y=outcome_m1)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Predicted Outcome for Feeding Model")
ggplot(data=grpyr_df, aes(x=net_density_wog, y=outcome_m1)) + geom_point()+labs(x = "Network Density", y="Outcome", title="Network Density vs. Predicted Outcome for Feeding Model")

grpyr_df$outcome_m2 <- predict(logis.model.moving, grpyr_df, type="response")
# Plot Predicted data and original data points
ggplot(data=grpyr_df, aes(x=n_adults, y=outcome_m2)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Predicted Outcome for Moving Model")
ggplot(data=grpyr_df, aes(x=net_density_wog, y=outcome_m2)) + geom_point()+labs(x = "Network Density", y="Outcome",  title="Network Density vs. Predicted Outcome for Moving Model")

grpyr_df$outcome_m3 <- predict(logis.model.feeding_per_moving, grpyr_df, type="response")
# Plot Predicted data and original data points
ggplot(data=grpyr_df, aes(x=n_adults, y=outcome_m3)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Predicted Outcome for Feeding Per Moving Model")
ggplot(data=grpyr_df, aes(x=net_density_wog, y=outcome_m3)) + geom_point()+labs(x = "Network Density", y="Outcome", title="Network Density vs. Predicted Outcome for Feeding Per Moving Model")

## RAW outcomes
grpyr_df<-grpyr_df%>%mutate(
  raw_outcome_m1=n_feeding/n_total_sample,
  raw_outcome_m2=n_feeding/n_total_sample,
  raw_outcome_m3=n_feeding/n_moving,
)

ggplot(data=grpyr_df, aes(x=n_adults, y=raw_outcome_m1)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Raw Outcome for Feeding Model")
ggplot(data=grpyr_df, aes(x=net_density_wog, y=raw_outcome_m1)) + geom_point()+labs(x = "Network Density", y="Outcome", title="Network Density vs. Raw Outcome for Feeding Model")
ggplot(data=grpyr_df, aes(x=n_adults, y=raw_outcome_m2)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Raw Outcome for Moving Model")
ggplot(data=grpyr_df, aes(x=net_density_wog, y=raw_outcome_m3)) + geom_point()+labs(x = "Network Density", y="Outcome",  title="Network Density vs. Raw Outcome for Moving Model")
ggplot(data=grpyr_df, aes(x=n_adults, y=raw_outcome_m3)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Raw Outcome for Feeding Per Moving Model")
ggplot(data=grpyr_df, aes(x=net_density_wog, y=raw_outcome_m3)) + geom_point()+labs(x = "Network Density", y="Outcome", title="Network Density vs. Raw Outcome for Feeding Per Moving Model")
```



### Model Diagonostics

```{r}
par(mfrow=c(2,2))
plot(logis.model.feeding)
```

```{r}
par(mfrow=c(2,2))
plot(logis.model.moving)
```

```{r}
par(mfrow=c(2,2))
plot(logis.model.feeding_per_moving)
```

