---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

#### 1. ACCESS BABASE
```{r}
#Open 'Utilities'>'Terminal'
#ssh -f mjc107@papio.biology.duke.edu -L 2222:localhost:5432 -N
#Install devtools if not already present
if (!("devtools" %in% installed.packages()[,"Package"]))
  install.packages("devtools")
# Install newest version of ramboseli if not already installed
devtools::install_github("amboseli/ramboseli")
#devtools::install_github("amboseli/ramboseli", ref = "ramboselitidyr-dev")
Sys.setenv(TZ = 'UTC')
list.of.packages <- list("foreach", "doSNOW", "parallel", "tidyverse",
                         "lubridate", "dbplyr", "purrrlyr", "RPostgreSQL",
                         "zoo", "ramboseli")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if (length(new.packages)) install.packages(unlist(new.packages))
lapply(list.of.packages, require, character.only = T)

# You will need to change user to your personal babase login AND get your password
# One approach to doing that is through Rstudio
# You could also just type it in your script, but that's not recommended for security.
babase <- DBI::dbConnect(RPostgreSQL::PostgreSQL(),
                           host = "localhost",
                           port = 2222,
                           user = "zf59",
                           dbname = "babase",
                           password = rstudioapi::askForPassword("Database password"))

```

#### 2. DATA MANAGEMENT

#### 2.1 LOAD BABASE TABLES

```{r}
#Connect to source functions
source("Functions.R")

# ---- LOAD DATAFRAMES ------------------------------------------------------
library(ramboseli)

# Database connections
biograph <- tbl(babase, "biograph")
members <- tbl(babase, "members")
maturedates <- tbl(babase, "maturedates")
rankdates <- tbl(babase, "rankdates")
maternities <- tbl(babase, "maternities")
actor_actees <- tbl(babase, "actor_actees")
samples_goff <- tbl(babase, "samples_goff")
groups_history <- tbl(babase, "groups_history")
# Get local copy of biograph table
biograph_l <- collect(tbl(babase, "biograph"))
#Get local copy of maternities table
maternities_l <- collect(tbl(babase, "maternities"))
#Get local copy of groups history table
groups_history_l <- collect(tbl(babase, "groups_history"))
#Get local copy of maturedates
maturedates_l <- collect(tbl(babase, "maturedates"))
#Get local copy of rankdates
rankdates_l <- collect(tbl(babase, "rankdates"))

# ---- JOIN DATAFRAMES ------------------------------------------------------
#Create connection version
# Join maturedates to biograph
md_females <- maturedates %>%
  semi_join(filter(biograph, sex == "F"), by = "sname")
# Join rankdates to biograph
rd_males <- rankdates %>%
  semi_join(filter(biograph, sex == "M"), by = "sname")
#Create local version of md_females and rd_males
# Join maturedates to biograph
md_females_l <- maturedates %>%
  semi_join(filter(biograph, sex == "F"), by = "sname") %>%
  collect()
# Join rankdates to biograph
rd_males_l <- rankdates %>%
  semi_join(filter(biograph, sex == "M"), by = "sname") %>%
  collect()

# ---- SUBSETTED DATASETS EXCLUDING BEHAVIORAL GAPS -------------------------
members_l <- subset_members(babase)
focals_l <- subset_focals(babase, members_l)
females_l <- subset_females(members_l)
grooming_l <- subset_interactions(babase, members_l, my_acts = c("G"))

# ---- LOAD PACKAGES -------------------------------------------------------

library(DHARMa)
library(tidyverse)
library(dbplyr)
library(data.table)
library(ggplot2)
library(cowplot)
library(corrplot)
library(vegan)
library(broom.mixed)
library(RcppRoll)
library(stringr)
library(network)
library(intergraph)
library(igraph)
# library(MuMIn)
library(reshape2) 
library(lubridate)
library(hrbrthemes)
library(viridis)
library(forcats)
library(coxme)
library(lme4)
library(car)
library(ggfortify)
library(survival)
library(survminer)
#library(MASS)
library(patchwork)
library(lmtest)

```

#### 2.2 CREATE DATASET

```{r}
# ---- GRP YEARS -------------------------------------------------------------
#Note: these grp years may need some revision after meetings with Susan and Laurence
# The rows should be:
#   - group years
#   - groups that were study groups during year of interest
#   - exclude group 1.3 (Proton's group
#   - first start date should be the date the grp became a study grp
#   - last end date can't occur after the last time the grp was a study grp
#Create df where group years are level of observation

groups <- groups_history_l %>%
  filter(gid < 3 & gid != 1.3) %>% #eliminate non-study groups
  filter(!is.na(first_study_grp_census)) %>% #Note: check why these are NA but listed as study groups
  dplyr::select(gid, name, permanent, impermanent, first_study_grp_census, last_reg_census, study_grp) %>%
  mutate(last_time_study_grp = fifelse(!is.na(last_reg_census), as.Date(last_reg_census), 
                                        fifelse(is.na(last_reg_census) & !is.na(impermanent), as.Date(impermanent), as.Date("2022-06-29")))) #create date telling last time grp was a study grp
#Create a start date for each group year
groups <- groups %>%
  mutate(startyear = fifelse(month(first_study_grp_census)==11 | month(first_study_grp_census)==12, as.numeric(format(first_study_grp_census,'%Y')) + 1, as.numeric(format(first_study_grp_census,'%Y'))))
  
groups$first_start <- as.Date(paste(groups$startyear, 11, 1), "%Y %m %d")
#Create a start date for each group year - if you want to start each year on day group first censused
start_dates <- groups %>%
  rowwise() %>%
  do(data.frame(gid=.$gid, start=seq(.$first_start,.$last_time_study_grp,by="1 year")))
#Create a start date for each group year - if you want to start each year on day group first censused
#start_dates <- groups %>%
#  rowwise() %>%
#  do(data.frame(gid=.$gid, start=seq(.$first_study_grp_census,.$last_time_study_grp,by="1 year")))
#Create group year df with start and end date for each year
group_years <- groups %>%
  dplyr::left_join(select(start_dates, "gid", "start"), by = "gid") %>% #join start dates
  mutate(end = start + years(1) - days(1),
         grp_year_length = end - start) %>%
  filter(end < last_time_study_grp) #end date can't occur after the last time the grp was a study grp

```

#### 3. CALCULATE VARIABLES FOR ANALYSIS

#### 3.1 NETWORK DENSITY AND GROUP SIZE

This is code I wrote to estimate network density and group size for a different analysis. In that analysis infant baboons were the level of observation and the start and end dates were a six month window during their early life. The df that held all my final data was called "subjects" which is here the equivalent of our "group_years" df. This code needs to be adapted to estimate network density for each group year.

n_adults = group size (we will also want to separate this by sex e.g., n_adults_female and n_adults_male)
net_density_wog = network density

Resources I used:
https://towardsdatascience.com/how-to-model-a-social-network-with-r-878b3a76c5a1
http://pablobarbera.com/big-data-upf/html/02a-networks-intro-visualization.html

```{r}
# ---- GRP SIZE AND NETWORK DENSITY -------------------------------------------------------------
# Find all adult members in each group on each date
adult_members <- members %>%
  filter(grp < 3 & grp != 1.3) %>%
  inner_join(dplyr::select(biograph, sname, sex), by = "sname") %>%
  left_join(dplyr::select(md_females, sname, matured), by = "sname") %>%
  left_join(dplyr::select(rd_males, sname, ranked), by = "sname") %>%
  filter((sex == "F" & date >= matured) | (sex == "M" & date >= ranked)) %>%
  collect()

#Network density without individuals with no grooms
grpyr_df <- group_years %>% 
  rowwise() %>% 
  mutate(sub_groom_df = list(subset_grooming(gid, start, end))) %>% 
  ungroup()
grpyr_df <- grpyr_df %>% 
  rowwise() %>% 
  mutate(sub_members_df = list(subset_adult_membership(gid, start, end))) %>% 
  ungroup()

#Count number of grooms in groups
grpyr_df <- grpyr_df %>%
  mutate(groom_rows = sapply(sub_groom_df, NROW)) %>% #Find number of rows in each sub_groom_df
  filter(groom_rows != "0") #eliminate grps with no grooms in their group due to behave gaps
#NOTE: This df still includes some behavioural gaps, where some grooming data has been recorded - we should decide what to do about these (we will control for observer effort later on)

#Count number of members in group >= 183 days to get group size
grpyr_df <- grpyr_df %>%
  mutate(n_adults = sapply(sub_members_df, NROW))
grpyr_df <- grpyr_df %>%
  mutate(net_density_wog = map2_dbl(sub_groom_df, sub_members_df, get_net_density_wog)) #network density including individuals with no grooms

#Join grpyr_df to subjects on mom_sname and end date
group_years <- group_years %>%
  left_join(dplyr::select(grpyr_df, gid, end, n_adults, net_density_wog, sub_members_df), by = c("gid", "end")) %>%
  mutate(net_density_wog = as.numeric(net_density_wog))

#### 1. Example network: Low network density
#Practice on one dataframe
#Subset grooming dataframe by group and time period
edges_sna_df <- subset(grooming_l, as.Date("2010-10-20") <= date & date <= as.Date("2011-10-19") & actor_grp==1.1100 & actee_grp==1.1100)
edges.df <- edges_sna_df %>%
  select(actor, actee) %>% #need actor, actee, total grooms
  mutate(pairs = paste(actor, actee))
edges.df <- edges.df %>%
  count(pairs) %>%
  mutate(actor = str_sub(pairs, 1, 3),
         actee = str_sub(pairs, 5, 7)) %>% 
  rename(weight = n) %>% 
  select(actor, actee, weight, -pairs)

#Create nodes df - Does include individuals with no grooms
nodes_sna_df <- subset(adult_members, as.Date("2010-10-20") <= date & date <= as.Date("2011-10-19") & grp==1.1100)
nodes.df <- nodes_sna_df %>%
  rename(name = sname) %>%
  distinct(name,.keep_all = TRUE) %>%
  select(name, sex)
nodes.df$id <- 1:nrow(nodes.df)
#my_network <- graph_from_data_frame(d=edges.df, vertices=nodes.df, directed=FALSE) #creates multiplex network
my_network <- graph_from_data_frame(d=edges.df, vertices=nodes.df, directed=TRUE)

#Plot example network
V(my_network)$color <- NA
males <- nodes.df %>% filter(sex == "M")
females <- nodes.df %>% filter(sex == "F")
V(my_network)$color[V(my_network)$name %in% males$name] <- "cyan4"
V(my_network)$color[V(my_network)$name %in% females$name] <- "darkseagreen2"
vertex_attr(my_network)
V(my_network)$size <- sqrt(strength(my_network)) * 1.1
set.seed(270)
fr <- layout_with_fr(my_network, niter=1000)
par(mar=c(0,0,0,0)); plot(my_network, layout=fr, vertex.label.color=c("black"))
title("", adj = 0, line = -1)
legend(x=.75, y=.85, legend=c("Male", "Female"), 
       pch=21, pt.bg=c("cyan4", "darkseagreen2"), pt.cex=2, bty="n")

#Calculate network density
my_network <- asNetwork(my_network)
network_density <- network::network.density(my_network)


# ---- GRP SIZE INCLUDING JUVENILES -------------------------------------------------------

# Find all members in each group on each date
all_members <- members %>%
  filter(grp < 3 & grp != 1.3 | !is.na(sname)) %>%
  inner_join(select(biograph, sname, sex), by = "sname") %>%
  collect()

#Subset members
grpyr_df <- grpyr_df %>% 
  rowwise() %>% 
  mutate(sub_all_members_df = list(subset_all_membership(gid, start, end))) %>% 
  ungroup()

#Count number of members in group >= 183 days to get group size
grpyr_df <- grpyr_df %>%
  mutate(n_members = sapply(sub_all_members_df, NROW))

#Join grpyr_df to subjects on mom_sname and end date
group_years <- group_years %>%
  left_join(select(grpyr_df, gid, end, n_members), by = c("gid", "end"))

```

#### 3.2 OBSERVER EFFORT

```{r}
# ---- OBSERVER EFFORT ------------------------------------------------------
#After 1999-10-04
#Grp focal minutes per adult
adult_focals <- samples_goff %>%
  filter(grp_of_focal < 3 & grp_of_focal != 1.3) %>%
  inner_join(select(biograph, sname, sex), by = "sname") %>%
  left_join(select(md_females, sname, matured), by = "sname") %>%
  left_join(select(rd_males, sname, ranked), by = "sname") %>%
  filter((sex == "F" & date >= matured) | (sex == "M" & date >= ranked)) %>%
  collect()

#Join to subjects - zeros because no focal data in samples_goff before 1999-10-04
group_years <- group_years %>%
  rowwise() %>%
  mutate(grp_focal_mins_post1999=get_focal_mins(adult_focals, start, end, gid))

#Before 1999-10-04 - Note: there are some imperfections in these data in babase
# Database connections
a1 <- tbl(babase, in_schema("babase_pending", "altos_points_84to96mar3")) %>%
  collect()
names(a1)[6:8] <- c("nn", "n1", "n2")
a1$n2 <- str_trim(a1$n2)
a2 <- tbl(babase, in_schema("babase_pending", "altos_points_96marto99")) %>%
  collect()
names(a2)[6:8] <- c("nn", "n1", "n2")
h1 <- tbl(babase, in_schema("babase_pending", "hooks_points_84to96")) %>%
  collect()
names(h1)[6:8] <- c("nn", "n1", "n2")
h2 <- tbl(babase, in_schema("babase_pending", "hooks_points_96to99")) %>%
  collect()
names(h2)[6:8] <- c("nn", "n1", "n2")

# Combine into one
samples_pre1999 <- bind_rows(select(a1, -mpos),
                  select(a2, -mpos),
                  select(h1, -mpos),
                  select(h2, -mpos))

#Create local version of members with behave gaps included
members_l3 <- collect(tbl(babase, "members"))

#Focal minute totals for individuals each hour
adult_focals_pre1999 <- samples_pre1999 %>%
  group_by(sname, date, time) %>%
  tally() %>%
  ungroup()

#Grp focal minutes per adult
adult_focals_pre1999 <- adult_focals_pre1999 %>%
  left_join(select(members_l3, sname, date, "grp_of_focal" = "grp"), by = c("sname", "date")) %>%
  filter(grp_of_focal < 3 & grp_of_focal != 1.3) 
adult_focals_pre1999 <- adult_focals_pre1999 %>%
  inner_join(select(biograph_l, sname, sex), by = "sname") %>%
  left_join(select(md_females_l, sname, matured), by = "sname") %>%
  left_join(select(rd_males_l, sname, ranked), by = "sname") %>%
  filter((sex == "F" & date >= matured) | (sex == "M" & date >= ranked)) %>%
  rename("minsis" = "n")  %>%
  collect()

#Join to subjects - focal data from before 1999-10-04
group_years <- group_years %>%
  rowwise() %>%
  mutate(grp_focal_mins_pre1999=get_focal_mins(adult_focals_pre1999, start, end, gid))

#Calculate group observation effort
group_years <- group_years %>%
  mutate(obs_effort = ifelse(start < as.Date("1999-10-04"), as.numeric(grp_focal_mins_pre1999)/n_adults, as.numeric(grp_focal_mins_post1999)/n_adults)) 
grpyr_df<-grpyr_df%>%
  dplyr::left_join(select(group_years, "gid", "start", "obs_effort"), by = c("gid", "start"))

# ---- CREATE RESIDUAL NETWORK DENSITY --------------------------------------------
#NOTE: This does not run because some individuals get NAs for observer effort - we need to look into why this is
#Make residual net density residuals
l1<- lm(scale(log(net_density_wog))~scale(log(obs_effort)),data=grpyr_df)
grpyr_df$net_density_wog_resid<- resid(l1)
#Group size vs network density
ggplot(grpyr_df, aes(x=n_adults, y=net_density_wog_resid)) +
      geom_point(size = 2.0, alpha = 0.7, colour="violetred4") +
      theme_cowplot() +
      ylab("Network density resid") +
      xlab("Group size") +
      geom_smooth(method=lm, colour="black", size=0.5)
p1.m <- lm(net_density_wog_resid ~ n_adults, data=grpyr_df)
#Group size vs observer effort
ggplot(grpyr_df, aes(x=n_adults, y=obs_effort)) +
      geom_point(size = 2.0, alpha = 0.7, colour="violetred4") +
      theme_cowplot() +
      ylab("Observer effort") +
      xlab("Group size") +
      geom_smooth(method=lm, colour="black", size=0.5)
p1.m <- lm(net_density_wog_resid ~ n_adults, data=grpyr_df)
#Network density vs observer effort
ggplot(grpyr_df, aes(x=net_density_wog, y=obs_effort)) +
      geom_point(size = 2.0, alpha = 0.7, colour="violetred4") +
      theme_cowplot() +
      ylab("Observer effort") +
      xlab("Network density") +
      geom_smooth(method=lm, colour="black", size=0.5)
p1.m <- lm(net_density_wog_resid ~ n_adults, data=grpyr_df)

```

#### 3.3 CALCULATE FORAGING EFFICIENCY

```{r}
# CALCULATE POINT SAMPLES
# Point sample data are in the old formats in babase_pending
# In four different tables, which oddly have different column names
# for proximity columns (so rename below)
a1 <- tbl(babase, in_schema("babase_pending", "altos_points_84to96mar3")) %>%
  collect()
names(a1)[6:8] <- c("nn", "n1", "n2")
a1$n2 <- str_trim(a1$n2)
a2 <- tbl(babase, in_schema("babase_pending", "altos_points_96marto99")) %>%
  collect()
names(a2)[6:8] <- c("nn", "n1", "n2")
h1 <- tbl(babase, in_schema("babase_pending", "hooks_points_84to96")) %>%
  collect()
names(h1)[6:8] <- c("nn", "n1", "n2")
h2 <- tbl(babase, in_schema("babase_pending", "hooks_points_96to99")) %>%
  collect()
names(h2)[6:8] <- c("nn", "n1", "n2")

# Combine into one
points_old <- bind_rows(select(a1, -mpos),
                        select(a2, -mpos),
                        select(h1, -mpos),
                        select(h2, -mpos))
#Get local copy of points after 1999
points_new <- collect(tbl(babase, "point_data"))
biograph <-collect(tbl(babase, "biograph"))
members <- collect(tbl(babase, "members"))
samples <- collect(tbl(babase, "samples"))
# ex_group<- grpyr_df[[13]][[1]]
# ex_group$start[1]
# ex_group$end[1]

## WORKING WITH NEW POINTS DATA
# total of point samples for a particular group year row
total_point_samples_gr_new<-function(sub_members_df){
    sub_members_df%>%
    left_join(samples, by="sname")%>%
    left_join(points_new, by ="sid")%>%
    filter(sex == "F")%>%
    filter(date>start&date<end)
}
count_total_new<-function(sub_members_df){
    total_point_samples_gr_new(sub_members_df)%>%
    group_by(sname)%>%
    count()
}
# time   spent   feeding: number of point samples from total sample adult females
count_feeding_new<-function(sub_members_df){
    total_point_samples_gr_new(sub_members_df)%>%
    filter(activity=="F")%>%
    group_by(sname)%>%
    count()
}
# time   spent   moving:  # of point samples from total sample adult females
count_moving_new<-function(sub_members_df){
    total_point_samples_gr_new(sub_members_df)%>%
    filter(activity=="W")%>%
    group_by(sname)%>%
    count()
}

# ## TEST WITH POINT SAMPLE NEW
# group_point <- ex_group%>%
#   left_join(samples, by="sname")%>%
#   left_join(points_new, by ="sid")%>%
#   filter(sex == "F")%>%
#   filter(date>start&date<end)%>%
#   filter(activity=="W")%>%
#   group_by(sname)%>%
#   count()
# count samples from points new in groupyear df

grpyr_df<-grpyr_df%>%
  rowwise() %>% 
  mutate(n_total_sample_new=sum(count_total_new(sub_members_df)$n))%>%
  mutate(n_feeding_new = sum(count_feeding_new(sub_members_df)$n))%>%
  mutate(n_moving_new = sum(count_moving_new(sub_members_df)$n))

## WORKING WITH NEW POINTS DATA
# total of point samples for a particular group year row
total_point_samples_gr_old<-function(sub_members_df){
    sub_members_df%>%
    left_join(points_old, by ="sname")%>%
    filter(sex == "F")%>%
    filter(date>start&date<end)
}
count_total_old<-function(sub_members_df){
    total_point_samples_gr_old(sub_members_df)%>%
    group_by(sname)%>%
    count()
}
# time   spent   feeding: number of point samples from total sample adult females
count_feeding_old<-function(sub_members_df){
    total_point_samples_gr_old(sub_members_df)%>%
    filter(act=="F")%>%
    group_by(sname)%>%
    count()
}
# time   spent   moving:  # of point samples from total sample adult females
count_moving_old<-function(sub_members_df){
    total_point_samples_gr_old(sub_members_df)%>%
    filter(act=="W")%>%
    group_by(sname)%>%
    count()
}
# count samples from points old in groupyear df
grpyr_df<-grpyr_df%>%
  rowwise() %>% 
  mutate(n_total_sample_old=sum(count_total_old(sub_members_df)$n))%>%
  mutate(n_feeding_old = sum(count_feeding_old(sub_members_df)$n))%>%
  mutate(n_moving_old = sum(count_moving_old(sub_members_df)$n))
grpyr_df<-grpyr_df%>%
  mutate(n_total_sample=n_total_sample_new+n_total_sample_old)%>%
  mutate(n_feeding=n_feeding_old+n_feeding_new)%>%
  mutate(n_moving=n_moving_old+n_moving_new)%>%
  select(-n_total_sample_old,-n_feeding_old,-n_moving_old,-n_total_sample_new, -n_feeding_new, -n_moving_new)

```

#### 3.4 WEATHER VARIABLES
```{r}
# ---- HYDRO YEAR ----------------------------------------------------------
#Get hydroyear of start date
grpyr_df<-grpyr_df%>%
  mutate(hydroyear = get_hydroyear(start))

# ---- RAINFALL ------------------------------------------------------------
amb_rain <- collect(tbl(babase, "min_maxs"))
# Take sum of measurements
amb_rain <- amb_rain %>%
  mutate(date_of = as.Date(wrdaytime)) %>%
  group_by(date_of) %>%
  summarise(rain = sum(rain, na.rm = TRUE)) 
grpyr_df<-grpyr_df%>%
  rowwise() %>%
  mutate(
    rain_normal = get_rain_normal(amb_rain, quo(date_of), quo(rain), start, end), 
    rain_total = get_rain_total(amb_rain, quo(date_of), quo(rain), start, end), 
    rain_anom_yr = rain_total - rain_normal, 
    rain_avg = get_rain_avg(amb_rain, start, end), 
    rain_div = get_rain_var(amb_rain, start, end)) %>%
  ungroup()

# ---- TEMPERATURE ---------------------------------------------------------
#Mean minimum temperature 
amb_temp <- tbl(babase, "min_maxs") %>%
  collect() %>%
  mutate(date = as.Date(wrdaytime)) %>%
  select(date, wstation, tempmin, tempmax)

# Deal with a couple of duplicated dates
amb_temp <- amb_temp %>%
  group_by(date, wstation) %>%
  summarise(tempmin = mean(tempmin, na.rm = TRUE)) %>%
  ungroup() %>%
  drop_na(tempmin)

# Generate full sequence of dates and fill with NA values
amb_temp <- amb_temp %>%
  complete(date = full_seq(date, 1))

grpyr_df <- grpyr_df %>%
  rowwise() %>%
  mutate(min_temp=get_min_temp(amb_temp, start, end))

#Mean maximum temperature 
amb_temp <- tbl(babase, "min_maxs") %>%
  collect() %>%
  mutate(date = as.Date(wrdaytime)) %>%
  select(date, wstation, tempmin, tempmax)

# Deal with a couple of duplicated dates
amb_temp <- amb_temp %>%
  group_by(date, wstation) %>%
  summarise(tempmax = mean(tempmax, na.rm = TRUE)) %>%
  ungroup() %>%
  drop_na(tempmax)

# Generate full sequence of dates and fill with NA values
amb_temp <- amb_temp %>%
  complete(date = full_seq(date, 1))

grpyr_df <- grpyr_df %>%
  rowwise() %>%
  mutate(max_temp=get_max_temp(amb_temp, start, end)) 


# ---- FIGURES WITH CORRELATIONS -------------------------------------------
#Create social measures to get correlations with rainfall measures
grpyr_df<-grpyr_df%>%
  mutate(pct_feeding=n_feeding/n_total_sample)%>%
  mutate(pct_moving=n_moving/n_total_sample)%>%
  mutate(pct_relative=n_feeding/n_moving)

# Calculate correlations - feeding
cor(grpyr_df$rain_anom_yr,grpyr_df$pct_feeding)
cor(grpyr_df$rain_avg,grpyr_df$pct_feeding)
cor(grpyr_df$rain_div,grpyr_df$pct_feeding)

# Calculate correlations - moving
cor(grpyr_df$rain_anom_yr,grpyr_df$pct_moving)
cor(grpyr_df$rain_avg,grpyr_df$pct_moving)
cor(grpyr_df$rain_div,grpyr_df$pct_moving)

# Calculate correlations - relative
cor(grpyr_df$rain_anom_yr,grpyr_df$pct_relative)
cor(grpyr_df$rain_avg,grpyr_df$pct_relative)
cor(grpyr_df$rain_div,grpyr_df$pct_relative)


# VISUALIZATION
ggplot(data=grpyr_df, aes(x=rain_avg, y=pct_feeding)) + geom_point()+labs(x = "Average Rainfall", y="Proportion of Time Spent Feeding", title = "Relationship of average rainfall vs. proportion of time spent feeding")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=rain_avg, y=pct_moving)) + geom_point()+labs(x = "Average Rainfall", y="Proportion of Time Spent Moving", title = "Relationship of average rainfall vs. proportion of time spent moving")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=rain_avg, y=pct_relative)) + geom_point()+labs(x = "Average Rainfall", y="Proportion of Time Spent Feeding Rel to Moving", title = "Relationship of average rainfall vs. proportion of time spent feeding relative to moving")+geom_smooth(method=lm, se=FALSE, col='blue')
```

#### 3.5 CALCULATE FORAGING EFFICIENCY PER FOOD TYPE

```{r}
# ex_group<- grpyr_df[[15]][[18]]
foodcodes <- collect(tbl(babase, "foodcodes"))
## WORKING WITH NEW POINTS DATA
total_point_samples_gr_new<-function(sub_members_df){
    sub_members_df%>%
    left_join(samples, by="sname")%>%
    left_join(points_new, by ="sid")%>%
    filter(sex == "F")%>%
    filter(date>start&date<end)
}
# time   spent  feeding on TTF
# count_feeding_new<-function(sub_members_df){
#     total_point_samples_gr_new(sub_members_df)%>%
#     filter(foodcode=="TTF")%>%
#     count()
# }
count_foodcode_new<-function(sub_members_df){
    count_foodcode<-total_point_samples_gr_new(sub_members_df)%>%
    group_by(foodcode)%>%
    count()%>%
    rename(fcode=foodcode)
    
    result<-count_foodcode%>%
    left_join(foodcodes, by="fcode")%>%
    ungroup%>%
    select(ftype,n)%>%
    group_by(ftype)%>%
    summarise(n = sum(n),
            .groups = 'drop')%>%
    as.data.frame()
    
    result_by_col <- result%>%pivot_wider(names_from=ftype, values_from=n)
    result_by_col
}

# foodcount_ex<-count_foodcode_new(ex_group)
# foodcount_ex%>%pivot_wider(names_from=ftype, values_from=n)
# count samples by food type in new dataframe
grpyr_df<-grpyr_df%>%
  rowwise()%>%
  mutate(foodtype_new=list(count_foodcode_new(sub_members_df)))


# old_group<- grpyr_df[[15]][[9]]
## WORKING WITH OLD POINTS DATA
total_point_samples_gr_old<-function(sub_members_df){
    sub_members_df%>%
    left_join(points_old, by ="sname")%>%
    filter(sex == "F")%>%
    filter(date>start&date<end)
}
count_foodcode_old<-function(sub_members_df){
    count_foodcode<-total_point_samples_gr_old(sub_members_df)%>%
    group_by(food)%>%
    count()%>%
    rename(fcode=food)
    
    result<-count_foodcode%>%
    left_join(foodcodes, by="fcode")%>%
    ungroup%>%
    select(ftype,n)%>%
    group_by(ftype)%>%
    summarise(n = sum(n),
            .groups = 'drop')%>%
    as.data.frame()
    
    result_by_col <- result%>%pivot_wider(names_from=ftype, values_from=n)
    result_by_col
}
grpyr_df<-grpyr_df%>%
  rowwise()%>%
  mutate(foodtype_old=list(count_foodcode_old(sub_members_df)))
# COMBINE OLD AND NEW TYPE DATA
combine_old_new<-function(a,b){
    union_all(a,b)%>%
    summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))
}
# TEST CODE (find the union between two dataframes)
# a<-grpyr_df[[30]][[67]]
# b<-grpyr_df[[30]][[72]]
# 
# union_all(a,b)%>%
#     summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))
grpyr_df<-grpyr_df%>%
  rowwise()%>%
  mutate(foodtype=list(combine_old_new(foodtype_old,foodtype_new)))%>%
  unnest(foodtype, names_repair = "minimal")


## GETTING the other food types for data new
#NVR (invertebrate), EDJ (elephant dung), GAR (garbage), VRT (vertebrates), WAX (water)
# ex_group<- grpyr_df[[15]][[18]]
select.me<-c('NVR','EDJ','GAR','VRT','WAX')
  
count_additionalfc_new<-function(sub_members_df){
    results<-total_point_samples_gr_new(sub_members_df)%>%
    group_by(foodcode)%>%
    count()%>%
    rename(fcode=foodcode)
    result_by_col<-results%>%
      pivot_wider(names_from=fcode, values_from=n)
    result_by_col[ , names(result_by_col) %in% select.me]
}
grpyr_df<-grpyr_df%>%
  rowwise()%>%
  mutate(additionalfc_new=list(count_additionalfc_new(sub_members_df)))
## GETTING the other food types for data old
old_group<- grpyr_df[[15]][[9]]
count_additionalfc_old<-function(sub_members_df){
    results<-total_point_samples_gr_old(sub_members_df)%>%
    group_by(food)%>%
    count()%>%
    rename(fcode=food)
    result_by_col<-results%>%
      pivot_wider(names_from=fcode, values_from=n)
    result_by_col[ , names(result_by_col) %in% select.me]
}
grpyr_df<-grpyr_df%>%
  rowwise()%>%
  mutate(additionalfc_old=list(count_additionalfc_old(sub_members_df)))
# COMBINE OLD AND NEW ADDITIONAL DATA
combine_additional<-function(a,b){
    union_all(a,b)%>%
    summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))
}
grpyr_df<-grpyr_df%>%
  rowwise()%>%
  mutate(foodtype=list(combine_additional(additionalfc_old,additionalfc_new)))%>%
  unnest(foodtype, names_repair = "minimal")
grpyr_df<-grpyr_df%>% select(-foodtype_new,-foodtype_old,-additionalfc_old,-additionalfc_new)


### Food type bar plot by group size
grpyr_df_ordered<-grpyr_df[order(grpyr_df$n_adults, decreasing = TRUE),]
grpyr_df_ordered<-grpyr_df_ordered[17:54]
grpyr_df_ordered<-grpyr_df_ordered%>%
  select(-net_density_wog,-obs_effort,-net_density_wog_resid,-n_total_sample,-n_feeding,-n_moving,-hydroyear,-rain_normal,-rain_total,-rain_anom_yr,-rain_avg,-rain_div,-pct_feeding)%>%
  
  select(-"NA")
q1<-grpyr_df_ordered[1:34,]
s1<-q1%>%summarize_if(is.numeric, sum, na.rm=TRUE)
q2<-grpyr_df_ordered[35:67,]
s2<-q2%>%summarize_if(is.numeric, sum, na.rm=TRUE)
q3<-grpyr_df_ordered[67:101,]
s3<-q3%>%summarize_if(is.numeric, sum, na.rm=TRUE)
q4<-grpyr_df_ordered[101:134,]
s4<-q4%>%summarize_if(is.numeric, sum, na.rm=TRUE)
## FOOD TYPE BY QUANTILES
df<-rbind(s1,s2,s3,s4)%>%
  select(-n_adults)
df$Quantile <- c("Quantile 1", "Quantile 2", "Quantile 3", "Quantile 4")
df<-df%>%pivot_longer(c(B,C,D,'F',G,K,L,O,P, 'T',X,R,NVR,WAX,EDJ,GAR,VRT), names_to="type")

# Stacked
ggplot(df, aes(fill=type, y=value, x=Quantile)) + 
    geom_bar(position="stack", stat="identity") +
    theme_cowplot() +
    ylab("total point samples") +
    xlab("group size quantile") +
    theme(legend.box.margin = margin(0, 0, 0, 12),
      legend.key.size = unit(0.5, 'cm'),
      legend.key.height = unit(0.5, 'cm'),
      legend.key.width = unit(0.5, 'cm'),
      legend.title = element_text(size=12),
      legend.text = element_text(size=12))
ggplot(df, aes(fill=type, y=value, x=Quantile)) + 
    geom_bar(position="fill", stat="identity") +
    theme_cowplot() +
    ylab("proportion of feeding time") +
    xlab("group size quantile") +
    theme(legend.box.margin = margin(0, 0, 0, 12),
      legend.key.size = unit(0.5, 'cm'),
      legend.key.height = unit(0.5, 'cm'),
      legend.key.width = unit(0.5, 'cm'),
      legend.title = element_text(size=12),
      legend.text = element_text(size=12))


### Food type bar plot by network density
grpyr_df_ordered<-grpyr_df[order(grpyr_df$net_density_wog_resid, decreasing = TRUE),]
grpyr_df_ordered<-grpyr_df_ordered[17:54]
grpyr_df_ordered<-grpyr_df_ordered%>%
  select(-n_adults,-obs_effort,net_density_wog,-n_total_sample,-n_feeding,-n_moving,-hydroyear,-rain_normal,-rain_total,-rain_anom_yr,-rain_avg,-rain_div,-pct_feeding)%>%
  
  select(-"NA")
q1<-grpyr_df_ordered[1:34,]
s1<-q1%>%summarize_if(is.numeric, sum, na.rm=TRUE)
q2<-grpyr_df_ordered[35:67,]
s2<-q2%>%summarize_if(is.numeric, sum, na.rm=TRUE)
q3<-grpyr_df_ordered[67:101,]
s3<-q3%>%summarize_if(is.numeric, sum, na.rm=TRUE)
q4<-grpyr_df_ordered[101:134,]
s4<-q4%>%summarize_if(is.numeric, sum, na.rm=TRUE)
## FOOD TYPE BY QUANTILES
df<-rbind(s1,s2,s3,s4)%>%
  select(-net_density_wog_resid)
df$Quantile <- c("Quantile 1", "Quantile 2", "Quantile 3", "Quantile 4")
df<-df%>%pivot_longer(c(B,C,D,'F',G,K,L,O,P, 'T',X,R,NVR,WAX,EDJ,GAR,VRT), names_to="type")

# Stacked
ggplot(df, aes(fill=type, y=value, x=Quantile)) + 
    geom_bar(position="stack", stat="identity")
    theme_cowplot() +
    ylab("total point samples") +
    xlab("network density resid quantile") +
    theme(legend.box.margin = margin(0, 0, 0, 12),
      legend.key.size = unit(0.5, 'cm'),
      legend.key.height = unit(0.5, 'cm'),
      legend.key.width = unit(0.5, 'cm'),
      legend.title = element_text(size=12),
      legend.text = element_text(size=12))
ggplot(df, aes(fill=type, y=value, x=Quantile)) + 
    geom_bar(position="fill", stat="identity") +
    theme_cowplot() +
    ylab("proportion of feeding time") +
    xlab("network density resid quantile") +
    theme(legend.box.margin = margin(0, 0, 0, 12),
      legend.key.size = unit(0.5, 'cm'),
      legend.key.height = unit(0.5, 'cm'),
      legend.key.width = unit(0.5, 'cm'),
      legend.title = element_text(size=12),
      legend.text = element_text(size=12))
```

#### 3.6 PREMLIMINARY DATA VISUALIZATIONS

```{r}
# ---- ADD OLRE AND POST-1999 VARIABLES -----------------------------------
grpyr_df$id <- seq.int(nrow(grpyr_df))

grpyr_df <- grpyr_df %>%
  mutate(post1999=ifelse(end > as.Date("1999-11-01"), 1, 0))

# ---- DATA DISTRIBUTION ---------------------------------------------------
#Feeding
dotchart(grpyr_df$n_feeding, xlab = "Count feeding",
         ylab = "Order of data", labels = F)
dotchart(grpyr_df$pct_feeding, xlab = "Proportion feeding",
         ylab = "Order of data", labels = F)

# ---- CORRELATION PLOTS ---------------------------------------------------
ggplot(data=grpyr_df, aes(x=n_adults, y=n_feeding/n_total_sample)) + geom_point()+labs(x = "Group Size", y="Proportion of Time Spent Feeding", title = "Relationship of group size vs. proportion of time spent feeding")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=net_density_wog_resid, y=n_feeding/n_total_sample)) + geom_point()+labs(x = "Network Density", y="Proportion of Time Spent Feeding", title = "Relationship of network density vs. proportion of time spent feeding")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=n_adults, y=n_moving/n_total_sample)) + geom_point()+labs(x = "Group Size", y="Proportion of Time Spent Moving", title = "Relationship of group size vs. proportion of time spent moving")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=net_density_wog_resid, y=n_moving/n_total_sample)) + geom_point()+labs(x = "Network Density", y="Proportion of Time Spent Moving", title = "Relationship of network density vs. proportion of time spent moving")+geom_smooth(method=lm, se=FALSE, col='blue')

# ---- HISTOGRAMS ----------------------------------------------------------
p3 <- ggplot(grpyr_df, aes(x=n_feeding/n_total_sample)) + geom_histogram(color="black", fill="white")+labs(x = "Prop time feeding", title = "Distribution of proportion of time spent feeding")
p4 <- ggplot(grpyr_df, aes(x=n_moving/n_total_sample)) + geom_histogram(color="black", fill="white")+labs(x = "Prop time moving", title = "Distribution of proportion of time spent moving")
p3+p4

```

#### 4. ANALYSIS

#### 4.1.1 FORAGING EFFICIENCY VS SOCIALITY (GLMM)

```{r}
# ---- MODELS GLMM ---------------------------------------------------------

# ---- TIME SPENT FEEDING --------------------------
logis.model.feeding<-glmer(cbind(n_feeding, (n_total_sample-n_feeding)) ~ scale(n_adults) +
                                                                          #I(scale(n_adults)^2) +
                                                                          #poly(n_adults, 2) +
                                                                          #scale(net_density_wog_resid) +
                                                                          scale(net_density_wog) +
                                                                          #I(scale(net_density_wog)^2) 
                                                                          #poly(net_density_wog, 2) +
                                                                          #scale(n_adults)*scale(net_density_wog) +
                                                                          scale(obs_effort) +
                                                                          scale(rain_avg) +
                                                                          post1999 +
                                                                          #scale(max_temp) +
                                                                          #(1|hydroyear:gid),
                                                                          #(1|id) +
                                                                          (1|gid) +
                                                                          (1|hydroyear),
                                                                          data=grpyr_df,
                                                                          glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)),
                                                                          family = "binomial" (link="logit"))
summary(logis.model.feeding)

library(jtools)
effect_plot(logis.model.feeding, pred = n_adults, interval = TRUE)
effect_plot(logis.model.feeding, pred = net_density_wog, interval = TRUE)
effect_plot(logis.model.feeding, pred = obs_effort, interval = TRUE)
effect_plot(logis.model.feeding, pred = rain_avg, interval = TRUE)
effect_plot(logis.model.feeding, pred = post1999, interval = TRUE)


# ---- TIME SPENT MOVING --------------------------
logis.model.moving<-glmer(cbind(n_moving, (n_total_sample-n_moving)) ~ scale(n_adults) +
                                                                        #I(scale(sqrt(n_adults))^2) +
                                                                        #poly(n_adults, 2) +
                                                                        scale(net_density_wog) +
                                                                        #poly(net_density_wog, 2) +
                                                                        #I(scale(sqrt(net_density_wog))^2) +
                                                                        #scale(n_adults)*scale(net_density_wog) +
                                                                        scale(obs_effort) +
                                                                        scale(rain_avg) +
                                                                        post1999 +
                                                                        #scale(max_temp) +
                                                                        #(1|hydroyear:gid),
                                                                        (1|gid) +
                                                                        #(1|id) +
                                                                        (1|hydroyear),
                                                                        #weight = n_total_sample,
                                                                        data=grpyr_df,
                                                                        glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)),
                                                                        family = "binomial" (link="logit"))

summary(logis.model.moving)

library(jtools)
effect_plot(logis.model.moving, pred = n_adults, interval = TRUE)
effect_plot(logis.model.moving, pred = net_density_wog, interval = TRUE)
effect_plot(logis.model.moving, pred = obs_effort, interval = TRUE)
effect_plot(logis.model.moving, pred = rain_avg, interval = TRUE)
effect_plot(logis.model.moving, pred = post1999, interval = TRUE)



# ---- TIME SPENT FEEDING VS MOVING ---------------------
logis.model.feeding_per_moving<-glmer(cbind(n_feeding, n_moving) ~ scale(n_adults) +
                                                                   #I(scale(n_adults)^2) +
                                                                   #poly(n_adults, 2) +
                                                                   scale(net_density_wog) +
                                                                   #I(scale(net_density_wog)^2) +
                                                                   #poly(net_density_wog, 3) +
                                                                   #scale(n_adults)*scale(net_density_wog) +
                                                                   scale(obs_effort) +
                                                                   scale(rain_avg) +
                                                                   post1999 +
                                                                   #scale(max_temp) +
                                                                   (1|gid) +
                                                                   #(1|id) +
                                                                   (1|hydroyear),
                                                                   data=grpyr_df,
                                                                   glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)),
                                                                   family = "binomial" (link="logit"))

summary(logis.model.feeding_per_moving)

library(jtools)
effect_plot(logis.model.feeding_per_moving, pred = n_adults, interval = TRUE)
effect_plot(logis.model.feeding_per_moving, pred = net_density_wog, interval = TRUE)
effect_plot(logis.model.feeding_per_moving, pred = obs_effort, interval = TRUE)
effect_plot(logis.model.feeding_per_moving, pred = rain_avg, interval = TRUE)
effect_plot(logis.model.feeding_per_moving, pred = post1999, interval = TRUE)


# ---- MODEL DIAGNOSTICS ---------------------------------------------------

simulationOutput <- simulateResiduals(fittedModel = logis.model.feeding, n = 250)
plot(simulationOutput) # Overall residual check
testDispersion(simulationOutput) # Overdispersion check
testUniformity(simulationOutput = simulationOutput) # Heteroscedasticity check
testZeroInflation(simulationOutput) # Zero inflation check
with(grpyr_df, plot(simulationOutput$scaledResiduals ~ scale(n_members)))
with(grpyr_df, plot(simulationOutput$scaledResiduals ~ scale(net_density_wog)))
with(grpyr_df, plot(simulationOutput$scaledResiduals ~ scale(obs_effort)))
with(grpyr_df, plot(simulationOutput$scaledResiduals ~ hydroyear))
## odds ratios and 95% CI on odds ratio - if 95% CI on OR includes 1 the predictor is not sig
#exp(cbind(OR = coef(logis.model.feeding), confint(logis.model.feeding)))

par(mfrow=c(2,2))
plot(logis.model.feeding)
dev.off()

resid<-resid(logis.model.feeding)
acf(resid)

simulationOutput <- simulateResiduals(fittedModel = logis.model.moving, n = 250)
plot(simulationOutput) # Overall residual check
testDispersion(simulationOutput) # Overdispersion check
testUniformity(simulationOutput = simulationOutput) # Heteroscedasticity check
testZeroInflation(simulationOutput) # Zero inflation check
with(grpyr_df, plot(simulationOutput$scaledResiduals ~ n_adults))
with(grpyr_df, plot(simulationOutput$scaledResiduals ~ net_density_wog))
## odds ratios and 95% CI on odds ratio - if 95% CI on OR includes 1 the predictor is not sig
#exp(cbind(OR = coef(logis.model.moving), confint(logis.model.moving)))

par(mfrow=c(2,2))
plot(logis.model.moving)
dev.off()

resid<-resid(logis.model.moving)
acf(resid)

simulationOutput <- simulateResiduals(fittedModel = logis.model.feeding_per_moving, n = 250)
plot(simulationOutput) # Overall residual check
testDispersion(simulationOutput) # Overdispersion check
testUniformity(simulationOutput = simulationOutput) # Heteroscedasticity check
testZeroInflation(simulationOutput) # Zero inflation check
with(grpyr_df, plot(simulationOutput$scaledResiduals ~ n_adults))
with(grpyr_df, plot(simulationOutput$scaledResiduals ~ net_density_wog))
## odds ratios and 95% CI on odds ratio - if 95% CI on OR includes 1 the predictor is not sig
#exp(cbind(OR = coef(logis.model.feeding_per_moving), confint(logis.model.feeding_per_moving)))

par(mfrow=c(2,2))
plot(logis.model.feeding_per_moving)
dev.off()

resid<-resid(logis.model.feeding_per_moving)
acf(resid)

# ---- MODEL VISUALIZATIONS -----------------------------------------------
# Fill predicted values using regression model
grpyr_df$outcome_m1 <- predict(logis.model.feeding, grpyr_df, type="response")
# Plot Predicted data and original data points
ggplot(data=grpyr_df, aes(x=n_adults, y=outcome_m1)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Predicted Outcome for Feeding Model")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=net_density_wog, y=outcome_m1)) + geom_point()+labs(x = "Network Density", y="Outcome", title="Network Density vs. Predicted Outcome for Feeding Model")+geom_smooth(method=lm, se=FALSE, col='blue')
grpyr_df$outcome_m2 <- predict(logis.model.moving, grpyr_df, type="response")
# Plot Predicted data and original data points
ggplot(data=grpyr_df, aes(x=n_adults, y=outcome_m2)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Predicted Outcome for Moving Model")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=net_density_wog, y=outcome_m2)) + geom_point()+labs(x = "Network Density", y="Outcome",  title="Network Density vs. Predicted Outcome for Moving Model")+geom_smooth(method=lm, se=FALSE, col='blue')
grpyr_df$outcome_m3 <- predict(logis.model.feeding_per_moving, grpyr_df, type="response")
# Plot Predicted data and original data points
ggplot(data=grpyr_df, aes(x=n_adults, y=outcome_m3)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Predicted Outcome for Feeding Per Moving Model")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=net_density_wog, y=outcome_m3)) + geom_point()+labs(x = "Network Density", y="Outcome", title="Network Density vs. Predicted Outcome for Feeding Per Moving Model")+geom_smooth(method=lm, se=FALSE, col='blue')
## RAW outcomes
grpyr_df<-grpyr_df%>%mutate(
  raw_outcome_m1=n_feeding/n_total_sample,
  raw_outcome_m2=n_feeding/n_total_sample,
  raw_outcome_m3=n_feeding/n_moving,
)
ggplot(data=grpyr_df, aes(x=n_adults, y=raw_outcome_m1)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Raw Outcome for Feeding Model")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=net_density_wog, y=raw_outcome_m1)) + geom_point()+labs(x = "Network Density", y="Outcome", title="Network Density vs. Raw Outcome for Feeding Model")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=n_adults, y=raw_outcome_m2)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Raw Outcome for Moving Model")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=net_density_wog, y=raw_outcome_m3)) + geom_point()+labs(x = "Network Density", y="Outcome",  title="Network Density vs. Raw Outcome for Moving Model")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=n_adults, y=raw_outcome_m3)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Raw Outcome for Feeding Per Moving Model")+geom_smooth(method=lm, se=FALSE, col='blue')
ggplot(data=grpyr_df, aes(x=net_density_wog, y=raw_outcome_m3)) + geom_point()+labs(x = "Network Density", y="Outcome", title="Network Density vs. Raw Outcome for Feeding Per Moving Model")+geom_smooth(method=lm, se=FALSE, col='blue')

```


#### 4.1.2 FOOD TYPES VS SOCIALITY (post-2000) (GLMM)

```{r}
# ---- MODELS GLMM ---------------------------------------------------------

#Eliminate years before food type data was available
grpyr_df_post2000 <- grpyr_df %>%
  subset(start > as.Date("2000-01-01"))

#Replace NAs for feeding counts with zeros
grpyr_df_post2000 <- grpyr_df_post2000 %>%
  mutate(B=ifelse(is.na(B), 0, B),
         C=ifelse(is.na(C), 0, C),
         D=ifelse(is.na(D), 0, D),
         F=ifelse(is.na(F), 0, F),
         G=ifelse(is.na(G), 0, G),
         K=ifelse(is.na(K), 0, K),
         L=ifelse(is.na(L), 0, L),
         O=ifelse(is.na(O), 0, O),
         P=ifelse(is.na(P), 0, P),
         T=ifelse(is.na(T), 0, T),
         NVR=ifelse(is.na(NVR), 0, NVR),
         WAX=ifelse(is.na(WAX), 0, WAX),
         EDJ=ifelse(is.na(EDJ), 0, EDJ)) %>%
  mutate(HighEnFoods=B+F+T)


# ---- TIME SPENT FEEDING ON CORMS ---------------

logis.model.corms<-glmer(cbind(C, n_feeding-C) ~ scale(n_adults) +
                                                 #I(scale(n_adults)^2) +
                                                 #poly(n_adults, 2) +
                                                 #scale(net_density_wog) +
                                                 poly(net_density_wog, 2) +
                                                 #I(scale(net_density_wog)^2) +
                                                 #scale(n_adults)*scale(net_density_wog) +
                                                 scale(obs_effort) +
                                                 scale(rain_avg) +
                                                 #post1999 +
                                                 #scale(max_temp) +
                                                 (1|gid) +
                                                 #(1|id) +
                                                 (1|hydroyear),
                                                 data=grpyr_df_post2000,
                                                 glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)),
                                                 family = "binomial" (link="logit"))
summary(logis.model.corms)

library(jtools)
effect_plot(logis.model.corms, pred = n_adults, interval = TRUE)
effect_plot(logis.model.corms, pred = net_density_wog, interval = TRUE)
effect_plot(logis.model.corms, pred = obs_effort, interval = TRUE)
effect_plot(logis.model.corms, pred = rain_avg, interval = TRUE)


# ---- TIME SPENT FEEDING ON HIGH ENERGY FOODS ---

logis.model.highen<-glmer(cbind(HighEnFoods, n_feeding-HighEnFoods) ~ #scale(n_adults) +
                                                 #I(scale(n_adults)^2) +
                                                 poly(n_adults, 2) +
                                                 #scale(net_density_wog) +
                                                 poly(net_density_wog, 2) +
                                                 #I(scale(net_density_wog)^2) +
                                                 #scale(n_adults)*scale(net_density_wog) +
                                                 scale(obs_effort) +
                                                 scale(rain_avg) +
                                                 #post1999 +
                                                 #scale(max_temp) +
                                                 (1|gid) +
                                                 #(1|id) +
                                                 (1|hydroyear),
                                                 data=grpyr_df_post2000,
                                                 glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)),
                                                 family = "binomial" (link="logit"))
summary(logis.model.highen)

library(jtools)
effect_plot(logis.model.highen, pred = n_adults, interval = TRUE)
effect_plot(logis.model.highen, pred = net_density_wog, interval = TRUE)
effect_plot(logis.model.highen, pred = obs_effort, interval = TRUE)
effect_plot(logis.model.highen, pred = rain_avg, interval = TRUE)


# ---- TIME SPENT FEEDING ON SEEDS ---------------

logis.model.seeds<-glmer(cbind(D, n_feeding-D) ~ scale(n_adults) +
                                                 #I(scale(n_adults)^2) +
                                                 #poly(n_adults, 2) +
                                                 #scale(net_density_wog) +
                                                 poly(net_density_wog, 2) +
                                                 #I(scale(net_density_wog)^2) +
                                                 #scale(n_adults)*scale(net_density_wog) +
                                                 scale(obs_effort) +
                                                 scale(rain_avg) +
                                                 #post1999 +
                                                 #scale(max_temp) +
                                                 (1|gid) +
                                                 #(1|id) +
                                                 (1|hydroyear),
                                                 data=grpyr_df_post2000,
                                                 glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)),
                                                 family = "binomial" (link="logit"))
summary(logis.model.seeds)

library(jtools)
effect_plot(logis.model.seeds, pred = n_adults, interval = TRUE)
effect_plot(logis.model.seeds, pred = net_density_wog, interval = TRUE)
effect_plot(logis.model.seeds, pred = obs_effort, interval = TRUE)
effect_plot(logis.model.seeds, pred = rain_avg, interval = TRUE)


# ---- TIME SPENT FEEDING ON INVERTEBRATES ---------------

logis.model.invert<-glmer(cbind(NVR, n_feeding-NVR) ~ scale(n_adults) +
                                                 #I(scale(n_adults)^2) +
                                                 #poly(n_adults, 2) +
                                                 scale(net_density_wog) +
                                                 #poly(net_density_wog, 2) +
                                                 #I(scale(net_density_wog)^2) +
                                                 #scale(n_adults)*scale(net_density_wog) +
                                                 scale(obs_effort) +
                                                 scale(rain_avg) +
                                                 #post1999 +
                                                 #scale(max_temp) +
                                                 (1|gid) +
                                                 #(1|id) +
                                                 (1|hydroyear),
                                                 data=grpyr_df_post2000,
                                                 glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)),
                                                 family = "binomial" (link="logit"))
summary(logis.model.invert)

library(jtools)
effect_plot(logis.model.invert, pred = n_adults, interval = TRUE)
effect_plot(logis.model.invert, pred = net_density_wog, interval = TRUE)
effect_plot(logis.model.invert, pred = obs_effort, interval = TRUE)
effect_plot(logis.model.invert, pred = rain_avg, interval = TRUE)


# ---- TIME SPENT FEEDING ON FRUITS ---------------
logis.model.fruit<-glmer(cbind(F, n_feeding-F) ~ #scale(n_adults) +
                                                 #I(scale(n_adults)^2) +
                                                 poly(n_adults, 2) +
                                                 scale(net_density_wog) +
                                                 #poly(net_density_wog, 2) +
                                                 #I(scale(net_density_wog)^2) +
                                                 #scale(n_adults)*scale(net_density_wog) +
                                                 scale(obs_effort) +
                                                 scale(rain_avg) +
                                                 #post1999 +
                                                 #scale(max_temp) +
                                                 (1|gid) +
                                                 #(1|id) +
                                                 (1|hydroyear),
                                                 data=grpyr_df_post2000,
                                                 glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)),
                                                 family = "binomial" (link="logit"))
summary(logis.model.fruit)

library(jtools)
effect_plot(logis.model.fruit, pred = n_adults, interval = TRUE)
effect_plot(logis.model.fruit, pred = net_density_wog, interval = TRUE)
effect_plot(logis.model.fruit, pred = obs_effort, interval = TRUE)
effect_plot(logis.model.fruit, pred = rain_avg, interval = TRUE)




# ---- MODEL DIAGNOSTICS ---------------------------------------------------

simulationOutput <- simulateResiduals(fittedModel = logis.model.corms, n = 250)
plot(simulationOutput) # Overall residual check
testDispersion(simulationOutput) # Overdispersion check
testUniformity(simulationOutput = simulationOutput) # Heteroscedasticity check
testZeroInflation(simulationOutput) # Zero inflation check
with(grpyr_df_post2000, plot(simulationOutput$scaledResiduals ~ n_adults))
with(grpyr_df_post2000, plot(simulationOutput$scaledResiduals ~ net_density_wog))
## odds ratios and 95% CI on odds ratio - if 95% CI on OR includes 1 the predictor is not sig
#exp(cbind(OR = coef(logis.model.corms), confint(logis.model.corms)))

par(mfrow=c(2,2))
plot(logis.model.corms)
dev.off()

simulationOutput <- simulateResiduals(fittedModel = logis.model.highen, n = 250)
plot(simulationOutput) # Overall residual check
testDispersion(simulationOutput) # Overdispersion check
testUniformity(simulationOutput = simulationOutput) # Heteroscedasticity check
testZeroInflation(simulationOutput) # Zero inflation check
with(grpyr_df_post2000, plot(simulationOutput$scaledResiduals ~ n_adults))
with(grpyr_df_post2000, plot(simulationOutput$scaledResiduals ~ net_density_wog))
## odds ratios and 95% CI on odds ratio - if 95% CI on OR includes 1 the predictor is not sig
#exp(cbind(OR = coef(logis.model.highen), confint(logis.model.highen)))

par(mfrow=c(2,2))
plot(logis.model.highen)
dev.off()

simulationOutput <- simulateResiduals(fittedModel = logis.model.seeds, n = 250)
plot(simulationOutput) # Overall residual check
testDispersion(simulationOutput) # Overdispersion check
testUniformity(simulationOutput = simulationOutput) # Heteroscedasticity check
testZeroInflation(simulationOutput) # Zero inflation check
with(grpyr_df_post2000, plot(simulationOutput$scaledResiduals ~ n_adults))
with(grpyr_df_post2000, plot(simulationOutput$scaledResiduals ~ net_density_wog))
## odds ratios and 95% CI on odds ratio - if 95% CI on OR includes 1 the predictor is not sig
#exp(cbind(OR = coef(logis.model.seeds), confint(logis.model.seeds)))

par(mfrow=c(2,2))
plot(logis.model.seeds)
dev.off()

simulationOutput <- simulateResiduals(fittedModel = logis.model.invert, n = 250)
plot(simulationOutput) # Overall residual check
testDispersion(simulationOutput) # Overdispersion check
testUniformity(simulationOutput = simulationOutput) # Heteroscedasticity check
testZeroInflation(simulationOutput) # Zero inflation check
with(grpyr_df_post2000, plot(simulationOutput$scaledResiduals ~ n_adults))
with(grpyr_df_post2000, plot(simulationOutput$scaledResiduals ~ net_density_wog))
## odds ratios and 95% CI on odds ratio - if 95% CI on OR includes 1 the predictor is not sig
#exp(cbind(OR = coef(logis.model.invert), confint(logis.model.invert)))

par(mfrow=c(2,2))
plot(logis.model.invert)
dev.off()

simulationOutput <- simulateResiduals(fittedModel = logis.model.fruit, n = 250)
plot(simulationOutput) # Overall residual check
testDispersion(simulationOutput) # Overdispersion check
testUniformity(simulationOutput = simulationOutput) # Heteroscedasticity check
testZeroInflation(simulationOutput) # Zero inflation check
with(grpyr_df_post2000, plot(simulationOutput$scaledResiduals ~ n_adults))
with(grpyr_df_post2000, plot(simulationOutput$scaledResiduals ~ net_density_wog))
## odds ratios and 95% CI on odds ratio - if 95% CI on OR includes 1 the predictor is not sig
#exp(cbind(OR = coef(logis.model.fruit), confint(logis.model.fruit)))

par(mfrow=c(2,2))
plot(logis.model.fruit)
dev.off()
```

#### 4.1.3 FORAGING EFFICIENCY VS SOCIALITY (GEE)

```{r}
#NOTE: PLOTS FOR THESE DON"T RUN YET BUT I STARTED WORKING ON THEM - FEEL FREE TO USE A DIFFERENT APPROACH TO PLOT THE RESULTS LIKE TO DISCUSSED FOR N_ADULTS AND NET_DENSITY_WOG

# ---- MODELS GEE -------------------------------------------------------------

#https://www.youtube.com/watch?v=qoqhPq_VILc
#https://www.youtube.com/watch?v=4qTZt1M17xY

library(geepack)

grpyr_df <- grpyr_df[order(grpyr_df$gid, grpyr_df$hydroyear),]
wav <- grpyr_df$hydroyear


# ---- TIME SPENT FEEDING --------------------------
foraging.gee.m <- geeglm(cbind(n_feeding+n_moving, n_total_sample-n_feeding-n_moving) ~ scale(n_adults) +
                                                                                        #I(scale(n_adults)^2) +
                                                                                        scale(net_density_wog) +
                                                                                        #I(scale(net_density_wog)^2) +
                                                                                        #scale(n_adults)*scale(net_density_wog) +
                                                                                        post1999 +
                                                                                        scale(obs_effort) +
                                                                                        scale(rain_avg),
                                                                                        #gid + 
                                                                                        #hydroyear,
                                                                                        #weights = n_total_sample,
                                                                                        data = grpyr_df,
                                                                                        corstr="ar1",
                                                                                        waves=wav,
                                                                                        family=binomial(logit), 
                                                                                        id=gid) 

#Plot raw values vs model pred - NOTE: THESE PLOTS DON'T RUN BECAUSE THERE NEEDS TO BE A PREDICTED SERIES OF VALUES FOR 'POST1999) (A BINARY VARIABLE)
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_adults = seq(from = 5,
                                   to = 50, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(foraging.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_adults, y = (grpyr_df$n_feeding+grpyr_df$n_moving)/grpyr_df$n_total_sample)
lines(pred1$n_adults, Pred2)

QIC(foraging.gee.m)

summary(foraging.gee.m)

cc <- coef(summary(foraging.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


# ---- TIME SPENT MOVING --------------------------
moving.gee.m <- geeglm(cbind(n_moving, n_total_sample-n_moving) ~ scale(n_adults) +
                                                                   #I(scale(n_adults)^2) +
                                                                   scale(net_density_wog) +
                                                                   #I(scale(net_density_wog)^2) +
                                                                   #scale(n_adults)*scale(net_density_wog) +
                                                                   post1999 +
                                                                   scale(obs_effort) +
                                                                   scale(rain_avg),
                                                                   #gid + 
                                                                   #hydroyear,
                                                                   #weights = n_total_sample,
                                                                   data = grpyr_df,
                                                                   corstr="ar1",
                                                                   waves=wav,
                                                                   family=binomial(logit), 
                                                                   id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_adults = seq(from = 5,
                                   to = 50, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(moving.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_adults, y = grpyr_df$pct_moving)
lines(pred1$n_adults, Pred2)

QIC(moving.gee.m)

summary(moving.gee.m)

cc <- coef(summary(moving.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


# ---- TIME SPENT FEEDING RELATIVE TO MOVING ---------------
feedmov.gee.m <- geeglm(cbind(n_feeding, n_moving) ~ scale(n_adults) +
                                                     #I(scale(n_adults)^2) +
                                                     scale(net_density_wog) +
                                                     #I(scale(net_density_wog)^2) +
                                                     #scale(n_adults)*scale(net_density_wog) +
                                                     post1999 +
                                                     scale(obs_effort) +
                                                     scale(rain_avg),
                                                     #gid + 
                                                     #hydroyear,
                                                     #weights = n_total_sample,
                                                     data = grpyr_df,
                                                     corstr="ar1",
                                                     waves=wav,
                                                     family=binomial(logit), 
                                                     id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_adults = seq(from = 5,
                                   to = 50, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(feedmov.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_adults, y = grpyr_df$n_feeding/grpyr_df$n_moving)
lines(pred1$n_adults, Pred2)

QIC(feedmov.gee.m)

summary(feedmov.gee.m)

cc <- coef(summary(feedmov.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)

```

##### Visualizations:

```{r}
# Fill predicted values using regression model
grpyr_df$outcome_m1 <- predict(foraging.gee.m, grpyr_df, type="response")
# Plot Predicted data and original data points
ggplot(data=grpyr_df, aes(x=n_adults, y=outcome_m1)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Predicted Outcome for Feeding Model")+geom_smooth()
ggplot(data=grpyr_df, aes(x=net_density_wog, y=outcome_m1)) + geom_point()+labs(x = "Network Density", y="Outcome", title="Network Density vs. Predicted Outcome for Feeding Model")+geom_smooth()

grpyr_df$outcome_m2 <- predict(moving.gee.m, grpyr_df, type="response")
# Plot Predicted data and original data points
ggplot(data=grpyr_df, aes(x=n_adults, y=outcome_m2)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Predicted Outcome for Moving Model")+geom_smooth()
ggplot(data=grpyr_df, aes(x=net_density_wog, y=outcome_m2)) + geom_point()+labs(x = "Network Density", y="Outcome",  title="Network Density vs. Predicted Outcome for Moving Model")+geom_smooth()

grpyr_df$outcome_m3 <- predict(feedmov.gee.m, grpyr_df, type="response")
# Plot Predicted data and original data points
ggplot(data=grpyr_df, aes(x=n_adults, y=outcome_m3)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Predicted Outcome for Feeding Per Moving Model")+geom_smooth()
ggplot(data=grpyr_df, aes(x=net_density_wog, y=outcome_m3)) + geom_point()+labs(x = "Network Density", y="Outcome", title="Network Density vs. Predicted Outcome for Feeding Per Moving Model")+geom_smooth()
```


#### 4.1.4 FOOD TYPES VS SOCIALITY (post-2000) (GEE)

```{r}
#NOTE: I ADDED CORMS AS AN EXAMPLE BUT CONTINUE FOR ALL THE MODELS IN 4.1.2 AS GEES

# ---- MODELS GEE ---------------------------------------------------------

#Eliminate years before food type data was available
grpyr_df_post2000 <- grpyr_df %>%
  subset(start > as.Date("2000-01-01"))

#Replace NAs for feeding counts with zeros
grpyr_df_post2000 <- grpyr_df_post2000 %>%
  mutate(B=ifelse(is.na(B), 0, B),
         C=ifelse(is.na(C), 0, C),
         D=ifelse(is.na(D), 0, D),
         F=ifelse(is.na(F), 0, F),
         G=ifelse(is.na(G), 0, G),
         K=ifelse(is.na(K), 0, K),
         L=ifelse(is.na(L), 0, L),
         O=ifelse(is.na(O), 0, O),
         P=ifelse(is.na(P), 0, P),
         T=ifelse(is.na(T), 0, T),
         NVR=ifelse(is.na(NVR), 0, NVR),
         WAX=ifelse(is.na(WAX), 0, WAX),
         EDJ=ifelse(is.na(EDJ), 0, EDJ)) %>%
  mutate(HighEnFoods=B+F+T)

grpyr_df_post2000 <- grpyr_df %>%
  subset(start > as.Date("2000-01-01")) %>%
  subset(end < as.Date("2010-11-01"))

grpyr_df_post2000 <- grpyr_df_post2000[order(grpyr_df_post2000$gid, grpyr_df_post2000$hydroyear),]
wav <- grpyr_df_post2000$hydroyear


# ---- TIME SPENT FEEDING ON CORMS ---------------

corms.gee.m <- geeglm(cbind(C, n_feeding-C) ~ scale(n_adults) +
                                              #I(scale(n_adults)^2) +
                                              scale(net_density_wog) +
                                              #I(scale(net_density_wog)^2) +
                                              #scale(n_adults)*scale(net_density_wog) +
                                              scale(obs_effort) +
                                              scale(rain_avg),
                                              #gid + 
                                              #hydroyear,
                                              #weights = n_total_sample,
                                              data = grpyr_df_post2000,
                                              corstr="ar1",
                                              waves=wav,
                                              family=binomial(logit), 
                                              id=gid) 

###ADD PLOTS HERE

QIC(corms.gee.m)

summary(corms.gee.m)

cc <- coef(summary(corms.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)

# ---- TIME SPENT FEEDING ON SEEDS ---------------

seeds.gee.m <- geeglm(cbind(D, n_feeding-D) ~ scale(n_adults) +
                                              #I(scale(n_adults)^2) +
                                              scale(net_density_wog) +
                                              #I(scale(net_density_wog)^2) +
                                              #scale(n_adults)*scale(net_density_wog) +
                                              scale(obs_effort) +
                                              scale(rain_avg),
                                              #gid + 
                                              #hydroyear,
                                              #weights = n_total_sample,
                                              data = grpyr_df_post2000,
                                              corstr="ar1",
                                              waves=wav,
                                              family=binomial(logit), 
                                              id=gid) 

# ---- TIME SPENT FEEDING ON VERTEBRATES ---------------


vertebrates.gee.m <- geeglm(cbind(NVR, n_feeding-NVR) ~ scale(n_adults) +
                                              #I(scale(n_adults)^2) +
                                              scale(net_density_wog) +
                                              #I(scale(net_density_wog)^2) +
                                              #scale(n_adults)*scale(net_density_wog) +
                                              scale(obs_effort) +
                                              scale(rain_avg),
                                              #gid + 
                                              #hydroyear,
                                              #weights = n_total_sample,
                                              data = grpyr_df_post2000,
                                              corstr="ar1",
                                              waves=wav,
                                              family=binomial(logit), 
                                              id=gid) 


# ---- TIME SPENT FEEDING ON FRUITS ---------------


fruits.gee.m <- geeglm(cbind(F, n_feeding-F) ~ scale(n_adults) +
                                              #I(scale(n_adults)^2) +
                                              scale(net_density_wog) +
                                              #I(scale(net_density_wog)^2) +
                                              #scale(n_adults)*scale(net_density_wog) +
                                              scale(obs_effort) +
                                              scale(rain_avg),
                                              #gid + 
                                              #hydroyear,
                                              #weights = n_total_sample,
                                              data = grpyr_df_post2000,
                                              corstr="ar1",
                                              waves=wav,
                                              family=binomial(logit), 
                                              id=gid) 
```

##### Visualizations:

```{r}
# Fill predicted values using regression model
grpyr_df$outcome_m1 <- predict(fruits.gee.m, grpyr_df, type="response")
# Plot Predicted data and original data points
ggplot(data=grpyr_df, aes(x=n_adults, y=outcome_m1)) + geom_point()+labs(x = "Group Size", y="Outcome", title="Group Size vs. Predicted Outcome for Fruit Model")+geom_smooth()
ggplot(data=grpyr_df, aes(x=net_density_wog, y=outcome_m1)) + geom_point()+labs(x = "Network Density", y="Outcome", title="Network Density vs. Predicted Outcome for Fruit Model")+geom_smooth()
```

#### TEST SECTION

```{r}
# VISUALIZATION
ggplot(data=grpyr_df, aes(x=obs_effort, y=n_feeding)) + geom_point()+labs(x = "Observation Effort", y="Number Samples Feeding", title = "")+geom_smooth(method=lm, se=FALSE, col='blue')

ggplot(data=grpyr_df, aes(x=obs_effort, y=n_total_sample)) + geom_point()+labs(x = "Observation Effort", y="Number Samples", title = "")+geom_smooth(method=lm, se=FALSE, col='blue')

ggplot(data=grpyr_df, aes(x=obs_effort, y=net_density_wog)) + geom_point()+labs(x = "Observation Effort", y="Network Density", title = "")+geom_smooth(method=lm, se=FALSE, col='blue')

ggplot(data=grpyr_df, aes(x=n_total_sample, y=net_density_wog)) + geom_point()+labs(x = "Number Samples", y="Network Density", title = "")+geom_smooth(method=lm, se=FALSE, col='blue')


# ---- MODELS GEE -------------------------------------------------------------

#https://www.youtube.com/watch?v=qoqhPq_VILc
#https://www.youtube.com/watch?v=4qTZt1M17xY

library(geepack)

#THIS IS CLOSE TO WHAT I THINK CATHERINE MARKHAM DID

grpyr_df_post2000 <- grpyr_df %>%
  subset(start > as.Date("2000-01-01")) %>%
  subset(end < as.Date("2010-11-01"))

grpyr_df_post2000 <- grpyr_df_post2000[order(grpyr_df_post2000$gid, grpyr_df_post2000$hydroyear),]
wav <- grpyr_df_post2000$hydroyear

feeding.gee.m <- geeglm((n_feeding+n_moving)/n_total_sample ~ scale(n_members) +
                                      #I(scale(n_adults)^2) +
                                      #scale(net_density_wog) +
                                      #I(scale(net_density_wog)^2) +
                                      #scale(n_adults)*scale(net_density_wog) +
                                      #scale(obs_effort) +
                                      scale(rain_avg) +
                                      scale(rain_div) +
                                      scale(max_temp),
                                      #gid + 
                                      #hydroyear,
                                      #weights = n_total_sample,
                                      data = grpyr_df_post2000,
                                      corstr="ar1",
                                      waves=wav,
                                      family=gaussian, 
                                      id=gid)

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_members = seq(from = 19,
                                   to = 103, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50),
                    rain_div = seq(from = 2.64,
                                          to = 3.86, length.out = 50),
                    max_temp = seq(from = 31.3,
                                          to = 34.6, length.out = 50))
fixe

#TEST WITH BINOMIAL MODEL
feeding.gee.m <- geeglm(cbind(n_feeding+n_moving, n_total_sample-n_feeding-n_moving) ~ scale(n_members) +
                                                                                       #I(scale(n_adults)^2) +
                                                                                       #scale(net_density_wog) +
                                                                                       #I(scale(net_density_wog)^2) +
                                                                                       #scale(n_adults)*scale(net_density_wog) +
                                                                                       #scale(obs_effort) +
                                                                                       scale(rain_avg) +
                                                                                       scale(rain_div) +
                                                                                       scale(max_temp),
                                                                                       #gid + 
                                                                                       #hydroyear,
                                                                                       #weights = n_total_sample,
                                                                                       data = grpyr_df_post2000,
                                                                                       corstr="ar1",
                                                                                       waves=wav,
                                                                                       family=binomial(logit), 
                                                                                       id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_members = seq(from = 19,
                                   to = 103, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50),
                    rain_div = seq(from = 2.64,
                                          to = 3.86, length.out = 50),
                    max_temp = seq(from = 31.3,
                                          to = 34.6, length.out = 50))
Pred2 <- predict(feeding.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df_post2000$n_members, y = (grpyr_df_post2000$n_feeding+grpyr_df_post2000$n_moving)/grpyr_df_post2000$n_total_sample)
lines(pred1$n_members, Pred2)


# ---- TIME SPENT FORAGING --------------------------

grpyr_df <- grpyr_df[order(grpyr_df$gid, grpyr_df$hydroyear),]
wav <- grpyr_df$hydroyear

###ALL MEMBER GRP SIZE

foraging.gee.m <- geeglm(cbind(n_feeding+n_moving, n_total_sample-n_feeding-n_moving) ~ scale(n_members) +
                                                                                        #I(scale(n_adults)^2) +
                                                                                        scale(net_density_wog) +
                                                                                        #I(scale(net_density_wog)^2) +
                                                                                        #scale(n_adults)*scale(net_density_wog) +
                                                                                        #post1999 +
                                                                                        scale(obs_effort) +
                                                                                        scale(rain_avg),
                                                                                        #gid + 
                                                                                        #hydroyear,
                                                                                        #weights = n_total_sample,
                                                                                        data = grpyr_df,
                                                                                        corstr="ar1", #AR1 has lowest QIC
                                                                                        waves=wav,
                                                                                        family=binomial(logit), 
                                                                                        id=gid)

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_members = seq(from = 13,
                                   to = 103, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(foraging.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_members, y = (grpyr_df$n_feeding+grpyr_df$n_moving)/grpyr_df$n_total_sample)
lines(pred1$n_members, Pred2)

QIC(foraging.gee.m)

summary(foraging.gee.m)

cc <- coef(summary(foraging.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


###ADULT GRP SIZE
foraging.gee.m <- geeglm(cbind(n_feeding+n_moving, n_total_sample-n_feeding-n_moving) ~ scale(n_adults) +
                                                                                        #I(scale(n_adults)^2) +
                                                                                        scale(net_density_wog) +
                                                                                        #I(scale(net_density_wog)^2) +
                                                                                        #scale(n_adults)*scale(net_density_wog) +
                                                                                        post1999 +
                                                                                        scale(obs_effort) +
                                                                                        scale(rain_avg),
                                                                                        #gid + 
                                                                                        #hydroyear,
                                                                                        #weights = n_total_sample,
                                                                                        data = grpyr_df,
                                                                                        corstr="ar1",
                                                                                        waves=wav,
                                                                                        family=binomial(logit), 
                                                                                        id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_adults = seq(from = 5,
                                   to = 50, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(foraging.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_adults, y = (grpyr_df$n_feeding+grpyr_df$n_moving)/grpyr_df$n_total_sample)
lines(pred1$n_adults, Pred2)

QIC(foraging.gee.m)

summary(foraging.gee.m)

cc <- coef(summary(foraging.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


# ---- TIME SPENT FEEDING --------------------------

###ALL MEMBERS GRP SIZE
feeding.gee.m <- geeglm(cbind(n_feeding, n_total_sample-n_feeding) ~ scale(n_members) +
                                                                     #I(scale(n_members)^2) +
                                                                     scale(net_density_wog) +
                                                                     #I(scale(net_density_wog)^2) +
                                                                     #scale(n_members)*scale(net_density_wog) +
                                                                     post1999 +
                                                                     scale(obs_effort) +
                                                                     scale(rain_avg),
                                                                     #gid + 
                                                                     #hydroyear,
                                                                     #weights = n_total_sample,
                                                                     data = grpyr_df,
                                                                     corstr="ar1",
                                                                     waves=wav,
                                                                     family=binomial(logit), 
                                                                     id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_members = seq(from = 13,
                                   to = 103, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(feeding.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_members, y = grpyr_df$pct_feeding)
lines(pred1$n_members, Pred2)

QIC(feeding.gee.m)

summary(feeding.gee.m)

cc <- coef(summary(feeding.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


###ADULT GRP SIZE
feeding.gee.m <- geeglm(cbind(n_feeding, n_total_sample-n_feeding) ~ scale(n_adults) +
                                                                     #I(scale(n_adults)^2) +
                                                                     scale(net_density_wog) +
                                                                     #I(scale(net_density_wog)^2) +
                                                                     #scale(n_adults)*scale(net_density_wog) +
                                                                     post1999 +
                                                                     scale(obs_effort) +
                                                                     scale(rain_avg),
                                                                     #gid + 
                                                                     #hydroyear,
                                                                     #weights = n_total_sample,
                                                                     data = grpyr_df,
                                                                     corstr="ar1",
                                                                     waves=wav,
                                                                     family=binomial(logit), 
                                                                     id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_adults = seq(from = 5,
                                   to = 50, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(feeding.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_adults, y = grpyr_df$pct_feeding)
lines(pred1$n_adults, Pred2)

QIC(feeding.gee.m)

summary(feeding.gee.m)

cc <- coef(summary(feeding.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)



# ---- TIME SPENT MOVING --------------------------

###ALL MEMBERS GRP SIZE
moving.gee.m <- geeglm(cbind(n_moving, n_total_sample-n_moving) ~ scale(n_members) +
                                                                  #I(scale(n_members)^2) +
                                                                  scale(net_density_wog) +
                                                                  #I(scale(net_density_wog)^2) +
                                                                  #scale(n_members)*scale(net_density_wog) +
                                                                  post1999 +
                                                                  scale(obs_effort) +
                                                                  scale(rain_avg),
                                                                  #gid + 
                                                                  #hydroyear,
                                                                  #weights = n_total_sample,
                                                                  data = grpyr_df,
                                                                  corstr="ar1",
                                                                  waves=wav,
                                                                  family=binomial(logit), 
                                                                  id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_members = seq(from = 13,
                                   to = 103, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(moving.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_members, y = grpyr_df$pct_moving)
lines(pred1$n_members, Pred2)

QIC(moving.gee.m)

summary(moving.gee.m)

cc <- coef(summary(moving.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


###ADULT GRP SIZE
moving.gee.m <- geeglm(cbind(n_moving, n_total_sample-n_moving) ~ scale(n_adults) +
                                                                   #I(scale(n_adults)^2) +
                                                                   scale(net_density_wog) +
                                                                   #I(scale(net_density_wog)^2) +
                                                                   #scale(n_adults)*scale(net_density_wog) +
                                                                   post1999 +
                                                                   scale(obs_effort) +
                                                                   scale(rain_avg),
                                                                   #gid + 
                                                                   #hydroyear,
                                                                   #weights = n_total_sample,
                                                                   data = grpyr_df,
                                                                   corstr="ar1",
                                                                   waves=wav,
                                                                   family=binomial(logit), 
                                                                   id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_adults = seq(from = 5,
                                   to = 50, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(moving.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_adults, y = grpyr_df$pct_moving)
lines(pred1$n_adults, Pred2)

QIC(moving.gee.m)

summary(moving.gee.m)

cc <- coef(summary(moving.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


# ---- TIME SPENT FEEDING RELATIVE TO MOVING ---------------

###ALL MEMBERS GRP SIZE
feedmov.gee.m <- geeglm(cbind(n_feeding, n_moving) ~ scale(n_members) +
                                                     #I(scale(n_members)^2) +
                                                     scale(net_density_wog) +
                                                     #I(scale(net_density_wog)^2) +
                                                     #scale(n_members)*scale(net_density_wog) +
                                                     post1999 +
                                                     scale(obs_effort) +
                                                     scale(rain_avg),
                                                     #gid + 
                                                     #hydroyear,
                                                     #weights = n_total_sample,
                                                     data = grpyr_df,
                                                     corstr="ar1",
                                                     waves=wav,
                                                     family=binomial(logit), 
                                                     id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_members = seq(from = 13,
                                   to = 103, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(feedmov.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_members, y = grpyr_df$n_feeding/grpyr_df$n_moving)
lines(pred1$n_members, Pred2)

QIC(feedmov.gee.m)

summary(feedmov.gee.m)

cc <- coef(summary(feedmov.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


###ADULT GRP SIZE
feedmov.gee.m <- geeglm(cbind(n_feeding, n_moving) ~ scale(n_adults) +
                                                     #I(scale(n_adults)^2) +
                                                     scale(net_density_wog) +
                                                     #I(scale(net_density_wog)^2) +
                                                     #scale(n_adults)*scale(net_density_wog) +
                                                     post1999 +
                                                     scale(obs_effort) +
                                                     scale(rain_avg),
                                                     #gid + 
                                                     #hydroyear,
                                                     #weights = n_total_sample,
                                                     data = grpyr_df,
                                                     corstr="ar1",
                                                     waves=wav,
                                                     family=binomial(logit), 
                                                     id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_adults = seq(from = 5,
                                   to = 50, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(feedmov.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_adults, y = grpyr_df$n_feeding/grpyr_df$n_moving)
lines(pred1$n_adults, Pred2)

QIC(feedmov.gee.m)

summary(feedmov.gee.m)

cc <- coef(summary(feedmov.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)




























feeding.gee.m <- geeglm(n_feeding ~ scale(n_adults) +
                                    #I(scale(n_adults)^2) +
                                    scale(net_density_wog) +
                                    #I(scale(net_density_wog)^2) +
                                    #scale(n_adults)*scale(net_density_wog) +
                                    scale(obs_effort) +
                                    scale(rain_avg),
                                    #gid + 
                                    #hydroyear,
                                    weights = n_total_sample,
                                    data = grpyr_df,
                                    corstr="exchangeable",
                                    #waves=wav,
                                    family=poisson, 
                                    id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_adults = seq(from = 5,
                                   to = 50, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 190,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 2.180, length.out = 50))
Pred2 <- predict(feeding.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df$n_adults, y = grpyr_df$n_feeding)
lines(pred1$n_adults, Pred2)



QIC(feeding.gee.m)

summary(feeding.gee.m)

cc <- coef(summary(feeding.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)
















# ---- MODELS MCMCGLMM ---------------------------------------------------------
library(broom.mixed)
library(nlme)
library(MCMCglmm)

data <- grpyr_df %>%
  dplyr::select(id, n_adults, net_density_wog, obs_effort, rain_avg, gid, hydroyear, n_feeding, n_total_sample)

data <- as.data.frame(data)

  #Specify prior
  k <- 8
  prior=list(
    B=list(mu=rep(0,k),V=gelman.prior(~ scale(n_adults) + I(scale(n_adults)^2) + scale(net_density_wog) + I(scale(net_density_wog)^2) + scale(n_adults)*scale(net_density_wog) + scale(obs_effort) + scale(rain_avg), data=data, scale=sqrt(1+1))),
    G=list(G1=list(V=1, nu=1, alpha.mu=0, alpha.V=100), G2=list(V=1, nu=1, alpha.mu=0, alpha.V=100)), 
    R=list(V=1, fix=1))
  
  #Run MCMCglmm
  feeding.MCMCglmm.m<-MCMCglmm(cbind(n_feeding, (n_total_sample-n_feeding)) ~ scale(n_adults) +
                                                                              I(scale(n_adults)^2) +
                                                                              scale(net_density_wog) +
                                                                              I(scale(net_density_wog)^2) +
                                                                              scale(n_adults)*scale(net_density_wog) +
                                                                              scale(obs_effort) +
                                                                              scale(rain_avg),
                                                                              random=~gid + hydroyear,
                                                                              data=data, 
                                                                              family = "multinomial2",
                                                                              #family=c("ordinal", "ordinal"),
                                                                              prior=prior, nitt=950001,thin=500,burnin=80000)
  
  #Diagnostics
  autocorr.diag(feeding.MCMCglmm.m$VCV)
  posterior.mode(feeding.MCMCglmm.m$VCV)
  HPDinterval(feeding.MCMCglmm.m$VCV) #Bayesian equivalent of confidence intervals: values of the estimates that bound 95% of the posterior distributions
  
  #Model diagnostics
  par(mfrow=c(2,2), mar=c(2,1,1,1), ask="N")#so you can see all 4 plots at once
  plot(feeding.MCMCglmm.m, ask="N")
  par(mfrow=c(1,1), ask="N")#to reset the graphic window to just one graph
  











logis.model.feeding<-glmer(cbind(n_feeding, (n_total_sample-n_feeding)) ~ scale(n_adults) +
                                                                          #I(scale(n_adults)^2) +
                                                                          #poly(n_adults, 2) +
                                                                          scale(net_density_wog) +
                                                                          #I(scale(net_density_wog)^2) +
                                                                          #scale(n_adults)*scale(net_density_wog) +
                                                                          scale(obs_effort) +
                                                                          scale(rain_avg) +
                                                                          #scale(max_temp) +
                                                                          (1|gid) +
                                                                          #(1|id) +
                                                                          (1|hydroyear),
                                                                          data=grpyr_df,
                                                                          glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)),
                                                                          family = "binomial" (link="logit"))
summary(logis.model.feeding)


# ---- MODEL DIAGNOSTICS ---------------------------------------------------
simulationOutput <- simulateResiduals(fittedModel = logis.model.feeding, n = 250)
plot(simulationOutput) # Overall residual check
testDispersion(simulationOutput) # Overdispersion check
testUniformity(simulationOutput = simulationOutput) # Heteroscedasticity check
testZeroInflation(simulationOutput) # Zero inflation check
with(grpyr_df, plot(simulationOutput$scaledResiduals ~ n_adults))
with(grpyr_df, plot(simulationOutput$scaledResiduals ~ net_density_wog))
## odds ratios and 95% CI on odds ratio - if 95% CI on OR includes 1 the predictor is not sig
#exp(cbind(OR = coef(logis.model.feeding), confint(logis.model.feeding)))

par(mfrow=c(2,2))
plot(logis.model.feeding)
dev.off()









# ---- MODELS GEE (FOOD TYPES) -------------------------------------------------------------

grpyr_df_post2000 <- grpyr_df %>%
  subset(start > as.Date("2000-01-01"))

grpyr_df_post2000 <- grpyr_df_post2000 %>%
  mutate(B=ifelse(is.na(B), 0, B),
         C=ifelse(is.na(C), 0, C),
         D=ifelse(is.na(D), 0, D),
         F=ifelse(is.na(F), 0, F),
         G=ifelse(is.na(G), 0, G),
         K=ifelse(is.na(K), 0, K),
         L=ifelse(is.na(L), 0, L),
         O=ifelse(is.na(O), 0, O),
         P=ifelse(is.na(P), 0, P),
         T=ifelse(is.na(T), 0, T),
         NVR=ifelse(is.na(NVR), 0, NVR),
         WAX=ifelse(is.na(WAX), 0, WAX),
         EDJ=ifelse(is.na(EDJ), 0, EDJ))


# ---- TIME SPENT FEEDING ON CORMS ---------------

###RELATIVE TO FEEDING
c.gee.m <- geeglm(cbind(C, n_feeding-C) ~ scale(n_members) +
                                                   #I(scale(n_members)^2) +
                                                   scale(net_density_wog) +
                                                   #I(scale(net_density_wog)^2) +
                                                   #scale(n_members)*scale(net_density_wog) +
                                                   #scale(n_members)*scale(rain_avg) +
                                                   #scale(net_density_wog)*scale(rain_avg) +
                                                   scale(obs_effort) +
                                                   scale(rain_avg),
                                                   #gid + 
                                                   #hydroyear,
                                                   #weights = n_total_sample,
                                                   data = grpyr_df_post2000,
                                                   corstr="exchangeable",
                                                   #waves=wav,
                                                   family=binomial(logit), 
                                                   id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_members = seq(from = 13,
                                   to = 103, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 365,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 1.999, length.out = 50))
Pred2 <- predict(c.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df_post2000$n_members, y = grpyr_df_post2000$C/grpyr_df_post2000$n_feeding)
lines(pred1$n_members, Pred2)
plot(x = grpyr_df_post2000$net_density_wog, y = grpyr_df_post2000$C/grpyr_df_post2000$n_feeding)
lines(pred1$net_density_wog, Pred2)

QIC(c.gee.m)

summary(c.gee.m)

cc <- coef(summary(c.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


###RELATIVE TO FORAGING
c.gee.m <- geeglm(cbind(C, n_moving+n_feeding-C) ~ scale(n_members) +
                                                   #I(scale(n_members)^2) +
                                                   scale(net_density_wog) +
                                                   #I(scale(net_density_wog)^2) +
                                                   #scale(n_members)*scale(net_density_wog) +
                                                   #scale(n_members)*scale(rain_avg) +
                                                   #scale(net_density_wog)*scale(rain_avg) +
                                                   scale(obs_effort) +
                                                   scale(rain_avg),
                                                   #gid + 
                                                   #hydroyear,
                                                   #weights = n_total_sample,
                                                   data = grpyr_df_post2000,
                                                   corstr="exchangeable",
                                                   #waves=wav,
                                                   family=binomial(logit), 
                                                   id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_members = seq(from = 13,
                                   to = 103, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 365,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 1.999, length.out = 50))
Pred2 <- predict(c.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df_post2000$n_members, y = grpyr_df_post2000$C/(grpyr_df_post2000$n_moving+grpyr_df_post2000$n_feeding))
lines(pred1$n_members, Pred2)
plot(x = grpyr_df_post2000$net_density_wog, y = grpyr_df_post2000$C/(grpyr_df_post2000$n_moving+grpyr_df_post2000$n_feeding))
lines(pred1$net_density_wog, Pred2)

QIC(c.gee.m)

summary(c.gee.m)

cc <- coef(summary(c.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


# ---- TIME SPENT FEEDING ON FRUITS RELATIVE TO FORAGING ---------------

###RELATIVE TO FEEDING
g.gee.m <- geeglm(cbind(G, n_feeding-G) ~ scale(n_members) +
                                                   #I(scale(n_members)^2) +
                                                   scale(net_density_wog) +
                                                   #I(scale(net_density_wog)^2) +
                                                   #scale(n_members)*scale(net_density_wog) +
                                                   #scale(n_members)*scale(rain_avg) +
                                                   #scale(net_density_wog)*scale(rain_avg) +
                                                   scale(obs_effort) +
                                                   scale(rain_avg),
                                                   #gid + 
                                                   #hydroyear,
                                                   #weights = n_total_sample,
                                                   data = grpyr_df_post2000,
                                                   corstr="exchangeable",
                                                   #waves=wav,
                                                   family=binomial(logit), 
                                                   id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_members = seq(from = 13,
                                   to = 103, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 365,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 1.999, length.out = 50))
Pred2 <- predict(g.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df_post2000$n_members, y = grpyr_df_post2000$G/grpyr_df_post2000$n_feeding)
lines(pred1$n_members, Pred2)
plot(x = grpyr_df_post2000$net_density_wog, y = grpyr_df_post2000$G/grpyr_df_post2000$n_feeding)
lines(pred1$net_density_wog, Pred2)

QIC(g.gee.m)

summary(g.gee.m)

cc <- coef(summary(g.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


###RELATIVE TO FORAGING
g.gee.m <- geeglm(cbind(G, n_moving+n_feeding-G) ~ scale(n_members) +
                                                   #I(scale(n_members)^2) +
                                                   scale(net_density_wog) +
                                                   #I(scale(net_density_wog)^2) +
                                                   #scale(n_members)*scale(net_density_wog) +
                                                   #scale(n_members)*scale(rain_avg) +
                                                   #scale(net_density_wog)*scale(rain_avg) +
                                                   scale(obs_effort) +
                                                   scale(rain_avg),
                                                   #gid + 
                                                   #hydroyear,
                                                   #weights = n_total_sample,
                                                   data = grpyr_df_post2000,
                                                   corstr="exchangeable",
                                                   #waves=wav,
                                                   family=binomial(logit), 
                                                   id=gid) 

#Plot raw values vs model pred
#create new covariate values within observed range for predictions
pred1 <- data.frame(n_members = seq(from = 13,
                                   to = 103, length.out = 50),
                    net_density_wog = seq(from = 0.1,
                                          to = 1, length.out = 50),
                    obs_effort = seq(from = 365,
                                     to = 5900, length.out = 50),
                    rain_avg = seq(from = 0.399,
                                     to = 1.999, length.out = 50))
Pred2 <- predict(g.gee.m, newdata = pred1, type = "response")
plot(x = grpyr_df_post2000$n_members, y = grpyr_df_post2000$G/(grpyr_df_post2000$n_moving+grpyr_df_post2000$n_feeding))
lines(pred1$n_members, Pred2)
plot(x = grpyr_df_post2000$net_density_wog, y = grpyr_df_post2000$G/(grpyr_df_post2000$n_moving+grpyr_df_post2000$n_feeding))
lines(pred1$net_density_wog, Pred2)

QIC(g.gee.m)

summary(g.gee.m)

cc <- coef(summary(g.gee.m))
citab <- with(as.data.frame(cc),
     cbind(lwr=Estimate-1.96*Std.err,
           upr=Estimate+1.96*Std.err))
rownames(citab) <- rownames(cc)


```
